%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Agenda}

Goal: Acheiving Peak Performance (in 6 steps, 3 S's and 3 C's)

\begin{itemize}
\item Practices (3 S's)
	\begin{itemize}
	\item Specialize
	\item Simplify
	\item Spiritualize
	\end{itemize}

\item Behaviors (3 C's)
	\begin{itemize}
	\item Clutter reduction
	\item Creativity
	\item Collaboration
	\end{itemize}
	
\item Applications
	\begin{itemize}
	\item Simplicity in business
	\item Simplicity in investing
	\end{itemize}	
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Section 1: Introduction}

\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Ch1 : A Peak into the Human Mind}
Mind's limitations:
\begin{itemize}
\item Brain cannot multi-task, for non-routine tasks (``The Mind is flat'' - Chater)
\item Biases: stereotypes, recency and anchoring biases.
\item Our memory is weak, retrieval is fuzzy.
\item Choices: Simple selection/decision needs lots of neural activity
\item These limitations affect decision making and make mind manipulatable.
\item ``Rashoman Effect'': human perceptions are subjective and not objective, e.g. picture: old lady nose or young lady face.
\item Due to these limitations, mind takes shortcuts, simplifies, heuristics, patterns, biases, cultural stereotypes, etc.
\item Remedies: repetitive practice molds brain for consistent outcomes. Others: simplicity, specialization and spiritualization.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Section 2: Solutions (3 S's)}

\end{center}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Ch2 : Discovering the World of Specialization}

\begin{itemize}
\item To be Specialist (10000 hrs Malcolm Gladwell, for 'kind' domains such as chess) or Generalist (for 'wicked' domains such a business) or be both, the 'T'.
\item `T': 
	\begin{itemize}
	\item One own core mastery skill
	\item Breadth of shallow skills in collaboration with partners
	\end{itemize}
\item Malcolm Gladwell: 10000 hrs guy: Its not talent but also need  social circumstances, relentless and purposeful practice, immense application and enabling environment.
\item Building deep focused expertize, Mastery
\item Harder to excel if you are doing 'should' and not 'must'.
\item How to specialize? (Greene):
	\begin{itemize}
	\item Apprenticeship under a master
	\item Creative-active, new ways to be original
	\item Mastery, the high level intuition.
	\end{itemize}
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Ch3 : How to Simplify Your Life}

\begin{itemize}
\item Simplicity: easy to understand, implement, sell and course-correct.
\item ``Simplicity is ultimate Sophistication'' (Apple II)
\item Simplification types through:
	\begin{itemize}
	\item Habits/process/method
		\begin{itemize}
		\item Habits take 40\% of decisions
		\item Have habits: reading, intense focused work in solitude, reqrdings oneself, seeking high quality input and criticism, well defined daily routine.		
		\end{itemize}	
	\item Principles/rules
		\begin{itemize}
		\item Specializing
		\item Be different, stand-out
		\item Combining originality and specialization with deliberate practice into a deep thought
		\end{itemize}		
	\end{itemize}
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Ch4 : Connecting with Your Inner-self }

\begin{itemize}
\item Spirituality: acknowledging that there is Inner-self (soul) separate from body.
\item More spiritual approaches, dealing with:
	\begin{itemize}
	\item Clutter: leave out material possessions and focus on self.
	\item Emotions: fears, anxieties. Need reflections.
	\item Deep focus: avoid distractions
	\end{itemize}
\item Principles:
	\begin{itemize}
	\item Frugality: avoid the unnecessary
	\item Positivity: forward looking frame of mind, transparency
	\end{itemize}
\item Practices:
	\begin{itemize}
	\item Meditation: a doorway to Spirituality, train for stable state of mind, results in stress relief, clarity of thoughts, greater focus, creative ideas, co-operativeness. Reverse count technique.
	\item Relentless Focus: ruthlessly avoid social media, distractions. Keep only assigned time-block for such activities.
	\end{itemize}	
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Section 3. Desirable Behaviors (3 C's)}

\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Ch5 : Reduce, Reduce, Reduce: Getting Rid of Clutter}

\begin{itemize}
\item Overuse of smart phones is causing loneliness, extremism, anxiety
\item After deciding Specialization, simplified working day and spiritualization, its time to declutter life
\item Sequential steps to reduce mental clutter:
	\begin{itemize}
	\item Start with goal(s): singular goal would be good. Bezos's `regret minimization framework'.
	\item Prioritize:  `optimal stopping': need to decide when to stop looking and grab the first best option which appears thereafter.
	\item Checklist: for planning and execution. 'Do-Confirm' and 'Read-Do' types.
	\item Cache memory for quick and frequent retrieval.
	\item Jotter: small notebook to keep jotting down ideas
	\item Reduce time spent on smart phone
	\end{itemize}
\item Go for one month digital fast (from Carl Newport)

\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Ch6 : Creativity \& Memory}

\begin{itemize}
\item Creativity: in your area of specialization, a deep desire to excel. 
\item Steps to Creativity:
	\begin{itemize}
	\item Read: for new ideas, why reinvent the wheel?
	\item Travel places:  explore the world, industries and job roles
	\item Interview: experts
	\item Work hard: with others, getting marginally better is ok.
	\item Memory: helps Creativity, SQRQS (Scan, Question,Read, Question, Scan ) for retention
	\end{itemize}
\item ToDos:
	\begin{itemize}
	\item Create extensive reading list, dedicate time block
	\item Make travel schedule to explore new places
	\item Find groups of people with similar interests and interact
	\item Improve your memory with techniques
	\end{itemize}

\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Ch7 : Collaboration}

\begin{itemize}
\item Leaders are facilitators. their role:
	\begin{itemize}
	\item Conflict resolution: remove deadlocks
	\item Situational leadership: adopt wrt people, situation
	\item Shared vision
	\item Maximize interaction opportunities
	\end{itemize}
\item Competitors cannot copy Collaboration!!
\item Work with rivals. Gandhi/Nehru had Dr Ambedkar in the ministry.
\item Checklist:
	\begin{itemize}
	\item  Work with colleagues from diverse backgrounds
	\item  Seek perspectives and viewpoints that are different from 
your
\item Align your personal development with the goals of your team
	\end{itemize}
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Ch8 : Simplicity in  Business}

\begin{itemize}
\item Why Simplify Business:
	\begin{itemize}
	\item Easy to follow, execute and self correcting!
	\item Unique, Original, Specialization
	\item Focus on one.
	\item Clear  standard operating procedures
	\item Common organizational goal
	\end{itemize}
\item Checklist:
	\begin{itemize}
	\item Define your organization’s goals and vision in simple terms
	\item Simplify your business offering
	\item Diverse backgrounds and bring a variety of experiences
	\end{itemize}
\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Ch9 : Simplicity in  Investing}

\begin{itemize}
\item Misconceptions on Investment:
	\begin{itemize}
	\item Only after taking higher risk you get higher returns.
	\item Lots of fuzzy ideas. Just need:  company gets high returns on capital and reinvests for higher returns.
	\end{itemize}
\item Allocate money based on your future goals: Security, Stability, Ambitions.
\item Coffee Can, 4 Simple criteria:
	\begin{itemize}
	\item 100 Cr market cap: from 6000 companies to 1500
	\item 10 years of existence (no new-age, startups)
	\item  10\% growth in sales/revenue consistent: generally  Banks $>$ 15\% loan book growth
	\item 15\% ROCE* growth  - Return on capital employed (pre-tax) : generally Bank $>$ 15\%
	\end{itemize} 
\end{itemize}

*ROCE $=$ EBIT$/$(long term debt $+$ shareholder equity)

\end{frame}