%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Notes from Naval Ravikant}

\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Stress}

	\begin{itemize}
	\item Stress happens when something wants to be in two places at one time. Like iron rod getting pulled from two ends.
	\item Stress is an inability to decide what’s important
	\item You want to find peace from mind. 
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Peace}

	\begin{itemize}
	\item Peace is happiness at rest.
	\item Happiness is Peace in motion.
	\item The ultimate goal is not happiness, even though we use that term a lot. The goal is peace.
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{How do you get to peace?}

	\begin{itemize}
	\item Fundamentally, peace is inactivity; it’s a sense that everything is fine.
	\item If everything is fine, you’re not doing any physical or mental activity to change it. 
	\item You’re also not wishing you were doing something to change it, because that creates stress. 
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{How do you get to peace?}

	\begin{itemize}
	\item You cannot work toward peace, only understanding
	\item ``The name of God is truth.''
	\item If/once you understand true nature of everything, then you are at Peace.
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Meditation}

	\begin{itemize}

	\item Free mind associates with things it sees, then imagines
	\item Contemplating on a subject, various aspects related to them
	\item Concentration is focusing on a topic
	\item Most meditation techniques are of concentration with a hope that at one stage you will be free from the concentration subject. 
	\item Meditation is actually beyond concentration. 
	\item You cannot do meditation. It happens when you are not doing anything. 
	\item Be still 1 hr a day. On one day you will reach a state where no thoughts bubble up.
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Life Formulas}

	\begin{itemize}

	\item Happiness = Health + Wealth + Good Relationships 
\item Health = Exercise + Diet + Sleep 
\item Exercise = High Intensity Resistance Training + Sports + Rest 
\item Diet = Natural Foods + Intermittent Fasting + Plants 
\item Sleep = No alarms + 8–9 hours + Circadian rhythms 
\item Wealth = Income + Wealth * (Return on Investment) 
\item Income = Accountability + Leverage + Specific Knowledge 
\item Accountability = Personal Branding + Personal Platform + Taking Risk? 
\item Leverage = Capital + People + Intellectual Property 
\item Specific Knowledge = Knowing how to do something society cannot yet easily train other people to do 
\item Return on Investment = ``Buy-and-Hold'' + Valuation + Margin of Safety
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Life Rules}

	\begin{itemize}
\item Be present above all else. 
\item Desire is suffering. (Buddha) 
\item Anger is a hot coal you hold in your hand while waiting to throw it at someone else. (Buddha) 
\item If you can't see yourself working with someone for life, don't work with them for a day. 
\item Reading (learning) is the ultimate meta-skill and can be traded for anything else. 
\item All the real benefits in life come from compound interest. 
\item Earn with your mind, not your time. 
\item 99 percent of all effort is wasted. 
\item Total honesty at all times. It's almost always possible to be honest and positive. 
\item Praise specifically, criticize generally. (Warren Buffett) 
\item Truth is that which has predictive power. 
\item Watch every thought. (Ask ``Why am I having this thought?'') 
\item All greatness comes from suffering. 
\item Love is given, not received. 
\item Enlightenment is the space between your thoughts. (Eckhart Tolle) 
\item Mathematics is the language of nature. 
\item Every moment has to be complete in and of itself.
	\end{itemize}

\end{frame}
