%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Notes of ``Directives'' and Books by Derek Sivers!!}

{\tiny https://sive.rs/d1, https://sive.rs/blog }


\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large How to be useful to others}
\end{center}

{\tiny https://sive.rs/d1u}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Get Famous}

\begin{itemize}
\item Do everything in public and for the public.
\item The more people you reach, the more useful you are.
\item The opposite is hiding, which is of no use to anyone.
\end{itemize}



\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Get Rich}

\begin{itemize}
\item Money is neutral proof you’re adding value to people’s lives.
\item So, by getting rich, you’re being useful as a side-effect.
\item Once rich, spend the money in ways that are even more useful to others.
\item Then getting rich is double-useful.
\end{itemize}


\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Share Strong Opinions}

\begin{itemize}
\item Money is neutral proof you’re adding value to people’s lives.
\item So, by getting rich, you’re being useful as a side-effect.
\item Once rich, spend the money in ways that are even more useful to others.
\item Then getting rich is double-useful.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Be Expensive}

\begin{itemize}
\item People given a placebo pill were twice as likely to have their pain disappear when told the pill was expensive.
\item People who paid more for tickets were more likely to attend the performance.
\item People who spend more for a product or service value it more, and get more use out of it.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large How to get rich}
\end{center}

{\tiny https://sive.rs/d1r}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Live Where Luck Strikes}

\begin{itemize}
\item Live where everything is happening,
\item where the money is flowing,
\item where careers are being made,
\item where your role models live.
\item Once there, be as in the game as anyone can be.
\item Be right in the middle of everything.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Say Yes to Everything}

\begin{itemize}
\item Meet everyone.
\item Pursue every opportunity.
\item Nothing is too small. Do it all.
\item Like lottery tickets, you never know which one will win. So the more, the better.
\item Follow-up and keep in touch with everyone.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Learn The Multiplying Skills}

\begin{itemize}
\item Speaking, writing, psychology, design, conversation, 2nd language, persuasion, programming, meditation/focus.
\item Not pursued on their own, they’re skills that multiply the success of your main pursuit.
\item (A pilot who’s also a great writer and public speaker.)
\item (A chef with a mastery of psychology, persuasion, and design.)
\item These skills multiply the results of your efforts, and give you an edge over others in your field.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Pursue Market Value Not Personal Value}

\begin{itemize}
\item Do what pays well.
\item Do not be the starving artist, working on things that have great personal value to you, but little market value.
\item Follow the money. It tells you where you’re most valuable.
\item Don’t try to make a career out of everything you love. For example, sex.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Shamelessly Imitate Success}

\begin{itemize}
\item Imitate the best strategies of your competitors.
\item The market doesn’t care about your personal need to be unique.
\item It’s selfless and humble to use the best ideas regardless of source, to create the best service or product for your clients.
\item Get great at executing other people’s ideas as well as your own.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Be The Owner, Not just Inventor}

\begin{itemize}
\item It’s tempting to try to be the ideas person, having someone else do the dirty work of making those ideas happen.
\item Ideas don’t make you rich. Great execution of ideas does.
\item A rule of capitalism: whoever takes the most financial risk gets the rewards.
\item The biggest rewards will always go to those that fund it and own it.
\item To get rich, be the owner. Own as close to 100\% as possible.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Benefit From Human Nature}

\begin{itemize}
\item Instead of complaining about the downside of human nature, find ways to benefit from it.
\item Instead of complaining about the rules, just learn the game, then play it.
\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large How to thrive in an Unknowable Future}
\end{center}

{\tiny https://sive.rs/d1t}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Prepare for the Worst}

\begin{itemize}
\item Since you have no idea what the future may bring, be open to the best and the worst.
\item But the best case scenario doesn’t need your preparation or your attention.
\item So mentally and financially prepare for the worst case, instead.
\item Like insurance, don’t obsess on it. Just prepare, then carry on appreciating the good times.
\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Expect Disaster}

\begin{itemize}
\item Every biography of a successful person has that line, “And then, things took a turn for the worse.”
\item Fully expect that disaster to come to you at any time.
\item Completely assume it’s going to happen, and make your plans accordingly.
\item Not just money, but health, family, freedom. Expect it all to disappear.
\item Besides, you appreciate things more when you know this may be your last time seeing them.
\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Own as Little as Possible}

\begin{itemize}
\item Depend on even less.
\item The less you own, the less you’re affected by disaster.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Choose Opportunity, Not Loyalty}

\begin{itemize}
\item Have no loyalty to location, corporation, or your past public statements.
\item Be an absolute opportunist, doing whatever is best for the future in the current situation, unbound by the past.
\item Have loyalty for only your most important human relationships.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Own as Little as Possible}

\begin{itemize}
\item The best plan is the one that lets you change your plans.
\item (Example: renting a house is buying the option to move at any time without losing money in a changing market.)
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Avoid Planning}

\begin{itemize}
\item For maximum options, don’t plan at all.
\item Since you have no idea how the situation or your mood may change in the future, wait until the last moment to make each decision.
\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large How to like people}
\end{center}

{\tiny https://sive.rs/d1p}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Assume it's their last day}

\begin{itemize}
\item Everyone talks about living like it’s your last day on earth.
\item Instead, to appreciate someone, live like it’s their last day on earth.
\item Treat them accordingly. Try to fulfill their dreams for the day.
\item Really listen to them. Learn from them.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Be Who You'd be when Alone}

\begin{itemize}
\item You could live in a crowd, pleasing only others.
\item You could live in solitude, pleasing only yourself.
\item But ideally, when in a crowd, be the same person you’d be when alone.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Assume Men and Women are the same}

\begin{itemize}
\item Men think women are so different from them.
\item Women think men are so different from them.
\item But the differences among men and differences among women are far greater than the differences between men and women.
\item So counteract your tendency to exaggerate the differences.
\item Assume men and women are the same.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Always Make New Friends}

\begin{itemize}
\item As you grow and change, old friends and family will be unintentionally invested in maintaining you as you were before.
\item Let go of people that don’t welcome and encourage your change.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Avoid Harming the Relationship}

\begin{itemize}
\item For long-term relationship success, it’s more effective than seeking the positive.
\item A friendship that may take years to develop can be ruined by a single action.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Act Calm and Kind}

\begin{itemize}
\item Regardless of how you feel.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Don't Try to Change them}

\begin{itemize}
\item \ldots unless they asked you to.
\item Don’t teach a lesson.
\item Stop trying to change people who don’t think they have a problem.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Find Wisdom in Your Opponents}

\begin{itemize}
\item Really engage those who think opposite of you.
\item You already know the ideas common on your own side.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Purge The Vampires}

\begin{itemize}
\item Get rid of people that drain you, that don’t make you feel good about yourself.
\item They make you hate all people.
\end{itemize}

\end{frame}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large What to do when you get successful}
\end{center}

{\tiny https://sive.rs/d1s}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Change Yes to ``Hell Yeah!'' or No}

\begin{itemize}
\item Once successful, you need to switch strategies.
\item To get successful, you had to say yes to everything.
\item Now if you continue doing that, you’ll drown in all the opportunities.
\item Now say no to anything that makes you say anything less than “Hell yeah!”
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Keep Momentum}

\begin{itemize}
\item The temptation is to take it easy.
\item But like swinging on jungle vines, if you stop that forward motion you can never get it back.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large How to stop being rich and happy}
\end{center}

{\tiny https://sive.rs/d1x}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Prioritize Lifestyle Design}

\begin{itemize}
\item You’ve made it, so it’s all about you, now. Make your dreams come true.
\item Shape your surroundings to please your every desire.
\item Make your immediate gratification the most important thing.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Chase That Comparison Moment}

\begin{itemize}
\item You have the old thing. You want the new thing. Yes! Do it! Be happy for a week.
\item Ignore the fact that the happiness only comes from the moment of comparison between the old and new.
\item Once you’ve had your new thing for a week, and it becomes the new norm, seek happiness from another new thing.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Buy, not Rent}

\begin{itemize}
\item Why rent a house, castle, boat, or car, when you can buy?
\item It’s not about the thing, it’s about identity. This shows who you are now.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Internalize Your New Status}

\begin{itemize}
\item You worked hard to get here. Celebrate. Relax.
\item Admit you are in a different class of people now, with different needs.
\item Understand there is no going back.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Be a Connoisseur}

\begin{itemize}
\item Learn what others say is the finest.
\item Insist on only the finest.
\item You will now be unhappy with anything but the finest.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Get To Know Your Possessions}

\begin{itemize}
\item Now that you own the best, it’s time to focus on what you’ve got.
\item Learn all about the features of your new possessions.
\item Spend more time getting your surround sound and heated floor just right.
\item Work out the solar panel charging of your Tesla car. This is important.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Acclimate To Comfort}

\begin{itemize}
\item Eliminate every discomfort from your life.
\item Blame others when the world seems hard, and is not living up to your standards.
\end{itemize}

\end{frame}


