%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Jottings from Talks, Tweets}

{\small Miscellaneous Authors }


\end{center}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Leo Babauta}

	\begin{itemize}
	\item Set your 3 MITs (Most Imprtant Tasks) each morning
	\item Single Task - focus your attention
	\item Zero Inbox (Work In Progress mails ok)
	\item Work while disconnected
	\item Keep your desk de-cluttered
	\item Stick to 5 sentences emails (make words powerful)
	\item Say NO to any commitment outside your goals
	\item Low information diet: emails + twice a day, 
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Sam Harris: Waking Up}

	\begin{itemize}
	\item Religion is primarily for social conduct, may have personal enhancement
	\item Spirituality is for humanity, universal, away from religion, deeper experience
	\item Mindfulness is a state of being clear, non-judgmental and un-distracted attention to the contents of consciousness (mind) whether pleasant or unpleasant.
	\item Mindfulness gives better, more skilled, perspective to look at things
	\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Dr BM Hegde}

	\begin{itemize}
	\item One should consume natural food in moderation 
	\item Sleep in pitch dark room 
	\item Electronic devices such as Television should be switched off and mobile phones shouldn’t be charged while sleeping. This is to avoid the presence of electromagnetic waves. 
	\item One should get up before sunrise 
	\item One should eat the last meal before 7pm
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Dr BM Hegde References}
	\begin{itemize}
	\item Secrets revealed: BP, Sugar, Cancer, Heart Stroke Healthy Lifestyle for Better Life : https://www.youtube.com/watch?v=r0rRgvhNy1U 
	\item The End of Capitalism - William Creeck (Article), Are We Nearing The End Of Capitalism?  https://www.youtube.com/watch?v=IE3t77AMITU  (not William Creeck, though)
	\item The World Is Too Much with Us https://en.wikipedia.org/wiki/The\_World\_Is\_Too\_Much\_with\_Us   
	\item The Golem : What You Should Know About Science - Harry Collins and Trevor Pinch (Book) https://www.researchgate.net/publication/238342346\_The\_Golem\_What\_You\_Should\_Know\_about\_Science 
	\item "Doctors going on strike will improve society's health for sure" - British Medical Journal (Article) https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1127364/ 
	\item "Is U.S. health really the best in the world?" - Barbara Starfield (Article) [JAMA - 2000: V. 284; Pg. 483] https://www.jhsph.edu/research/centers-and-institutes/johns-hopkins-primary-care-policy-center/Publications\_PDFs/A154.pdf 
	\item "The end of the disease era" - Mary Tinetty (Article) [Archives of Internal Medicine - 2004: V. 116; Pg. 179] https://stallseniormedical.com/wp-content/uploads/The-End-of-the-Disease-Era-Tinetti.pdf 
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Dr BM Hegde References}
	\begin{itemize}
	\item "Matter is not made out of matter" - Hans Peter Durr (Article)
	\item Uncertainty Principle - Werener Heisenberg (Theory)
	\item Occult Chemistry - Annie Besant (Book) https://ia800301.us.archive.org/29/items/occultchemistryc00besa/occultchemistryc00besa.pdf 
	\item Molecules of Emotion - Candace Pert (Book) https://www.youtube.com/playlist?list=PL7aNzLFRfhm3c4V\_SfPsr0DRNPE1XAgAR 
	\item Quantum Doctor - Amit Goswami (Book) https://www.youtube.com/watch?v=eIpSui-wjPk 
	\item Inventing the AIDS virus - Peter H. Deusberg (Book) https://en.wikipedia.org/wiki/Inventing\_the\_AIDS\_Virus  https://www.youtube.com/watch?v=8FLXoDu\_ZDs 
	\item When Breath Becomes Air - Paul Kalanidhi (Book) https://www.youtube.com/watch?v=nTrMgBPZJHA 
	\item Affluent Society - John Kenneth Galbraith (Book)  https://en.wikipedia.org/wiki/The\_Affluent\_Society https://www.youtube.com/watch?v=FhMq6oPD1eM 
	\item Anatomy of an Illness - Norman Cousins (Book) https://www.youtube.com/watch?v=0LwKd68S15I 
	\item The Placebo Effect - Bingel et al (Article) [Science Translational Medicine - 2011: V. 3; Pg. 70] http://stm.sciencemag.org/content/3/70/70ra14 
	\item What Doctors Don't Get to Study in Medical School - B.M. Hegde (Book) https://www.youtube.com/watch?v=yA\_zy1lnlN4 
	\item Dementia: A drug-induced crime on mankind - Grace Elizabeth Jackson (Book)  https://beyondmeds.com/2009/06/08/drug-induced-dementia/   https://www.youtube.com/watch?v=lpsjwe69QFE 
	\item Pure, White and Deadly - John Yudkin (Book)
	\item Closing of an American Mind - Alan Bloom (Book) https://en.wikipedia.org/wiki/The\_Closing\_of\_the\_American\_Mind  https://www.youtube.com/watch?v=-15fOEovI0o 
	\item Science without Sense - Steven Milloy (Book)  https://ia600807.us.archive.org/14/items/milloy\_risky/milloy\_risky.pdf 
	\item  www.archimedesmodel.com
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Make Time: ??}
	\begin{itemize}
	\item Remove distracting apps (from your phone)
	\item Declutter Phone/Laptop screen
	\item What Will Be the Highlight of Your Day?
	\item For five days, a team would cancel all meetings and focus on solving a single problem, following a specific checklist of activities
	\item Something magic happens when you start the day with one high-priority goal.
	\item We got more done when we banned devices
	\item A healthy lunch, a quick walk, frequent breaks, and a slightly shorter workday helped maintain peak energy
	\item Highlight: Start Each Day by Choosing a Focus
	\item Laser: Beat Distraction to Make Time
	\item Energize: Use the Body to Recharge the Brain
	\item Reflect: Adjust and Improve Your System
	\item Newspaper: Schedule time once a week , emails twice a day 10am/5pm
	\item Get Better Sleep
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Make Time: ??}
	\begin{itemize}
	\item Walk to Work
	\item Eat Fat for Breakfast
	\item Stand Most of the Time
	\item Take Breaks Without Screens
	\item Do a Quick But Intense Workout
	\item Do the Chores
	\item One Thing at a Time
	\item Focus: focus on just one thing per month, or per year, we can make big changes to our health, career, relationships, finances, or any other department of life.
	\item Stuck? Switch to Play Mode
	\item Put your most important project on the front burner
	\item Put your second most important project on the back burner
	\item Make a kitchen sink for the rest
	\item World class performance comes after 10,000 hours of deliberate practice, 12,500 hours of deliberate rest, and 30,000 hours of sleep.
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Gut Health - Ben Warren's top 10 tips for a healthy gut.}

	\begin{itemize}
	\item Food/dairy intolerance causing Back pain, difficultly nose breathing, 
	\item IGG IGE test for whey protein, lactose/milk intolerance
	\item Most of the immune system is in stomoch as it has to prottect from outside food.
	\item It decides which protein to keep (food) and which to destroy (virus/bacteria are proteins too!!)
	\item Gluten in some folks gets identified as virus and immune reactions happen.
	\item Leaky gut affects body
	\item Auto immune: immune system goes hyper and attacks good parts of internal body
	\item Gut-brain axis : 3 way intersection of brain, gut and microbiome.
	\item For digestion, mental relaxation is needed. Control breathing, diaphragmatic, while eating.
	\item Chew food to liquid
	\item Apple cider before meal (if there isn't strong acid, this will help. If you already have it, then you can stop and take bicarbonate soda) same in case acid reflux.
	\item Start day with warm water + lemon. Gets stomach ready for the day
	\item If at all you need dairy products, take as raw as possible. Avoid if possible.
	\item Gluten (wheat, maida, etc) and Lactose (dairy) are to be avoided.
	\item Eat fermented food daily, probiotic
	\end{itemize}

\end{frame}

	

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Chris Bailey}

	\begin{itemize}
	\item Schedule time to completely disconnect from work
	\item Use visualizations to become more productive
	\item Capture all of the open loops in your head
	\item When you meet someone, shut off phone completely
	\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Avinash Dharmadhikari}

	\begin{itemize}
	\item Know thy-self - Ongoing
	\item Chose career of favorite topic - CAD
	\item Excellence and Creativity in the chosen topic
	% \item \textmarathi{विषय कळलेला पाहिजे ज्ञानावर पकड}. 
	% \item Yog \textmarathi{आसने, सूर्यनमस्कार, प्राणायाम, ध्यान}
	% \item \textmarathi{स्वाधाय : कोणताही विषय समोर आला तरी त्याचा अभ्यास करण्याचे कौशल्य}. Notes, Ref Cards
	\item Good command over English, Bilungual, Finance.
	\item Awareness of latest trends of your work.
	\item Entrepreneur in my field.  Teacher prepares students
	\item Creator of wealth (value addition to the topic)  
	% \item \textmarathi{वैश्विकता}: Do things at par with global standards
	\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{The book of YOGA - Christina Brown}

	\begin{itemize}
	\item Yoga is a state of mind. Stillness fosters awareness.
	\item Physical exercises still the body. Breath to focus the mind
	\item Relaxation to quieten the body and mind
	\item Chanting to arouse and then calm emotions
	\item Meditation to center the spirits.
	\item Yoga postures bring strength to the weak areas and soften the tight spots.
	% \item \textmarathi{अभ्यास }: Repeated study/effort, then becomes effortless
	% \item  \textmarathi{आसन} builds and controls \textmarathi{प्राण}- the vital force
	% \item Mind is the master of senses and the breath is the master of the Mind.
	% \item When the breath flows steadily your \textmarathi{आसन }becomes closer to perfect
	\item Frequently check your breathing
	\item Finding the quietness that lies within yourself
	\item Push your boundaries every time. Don't overdo it.
	\end{itemize}

\end{frame}


% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{frame}[fragile]\frametitle{The book of YOGA - Christina Brown}

	% \begin{itemize}
	% \item \textmarathi{यम }: Compassion for all beings. \textmarathi{अहिंसा }(tolerance, kindness), \textmarathi{सत्य, अस्तेय} (stealing), \textmarathi{ब्रह्मचर्य} (moderation) \textmarathi{अपरिग्रह}(non-accumulation, simplicity)
	% \item \textmarathi{नियम : शौच}(purity), \textmarathi{संतोष} (contentment), तप (dedication/fire-determiniation), \textmarathi{स्वाध्याय, ईश्वर-प्रणिधान}
	% \item \textmarathi{आसन}  (postures)
	% \item \textmarathi{प्राणायाम }(breath control)
	% \item  \textmarathi{प्रत्याहार} (withdrawal of senses)
	% \item \textmarathi{धारणा} (concentration, mindfulness, paying attention)
	% \item \textmarathi{ध्यान} (meditation)
	% \item \textmarathi{समाधी}
	% \item Start and End any activity with relaxation
	% \item Let it go, detachment. Tense and then relax parts one by one.
	% \item Stay Still and Don't worry
	% \end{itemize}

% \end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Maria Popova}

	\begin{itemize}
	\item  The secret of happiness: ``Find something more important than you are'' - philosopher Dan Dennett
	\item Don't go after prestigious positions, HoD, on committees etc. Waste of time.
	\item Steve Jobs:  And the only way to do great work is to love, what you do. If you haven't found it yet, keep looking. Don't settle
	\item The whole future lies in uncertainty: live immediately.
	\item No activity can be successfully pursued by an individual who is preoccupied 
	\item 7 Learnings:
		\begin{itemize}
		\item Allow yourself the uncomfortable luxury of changing your mind.
		\item Do nothing for prestige or status or money or approval alone. Have goal more than the promotion!!
		\item Be generous. With your time.
		\item Build pockets of stillness into your life. Sleep.
		\item Don't believe what others say about you
		\item Presence is far more intricate and rewarding an art than productivity.
		\item Expect anything worthwhile to take a long time
		\end{itemize}
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Uma Naidoo}


	\begin{itemize}
\item  Theme: Nutritional Psychiatry (Food Mood)
\item  Anxiety: Foods to avoid: gluten, sugar, processed veg oil (fried stuff outside-home), artificial sweeteners (cold drinks/soda)
\item  Hypoglycemia: keto diet may help
\item  Dementia/Brain-fog: Foods to have: 
	\begin{itemize}

	\item  Turmeric+black pepper, Cinnamon, saffron, rosemary, ginger
	\item  Olive oil + onions, garlic ( good pre-biotics)
	\item  Juniper berries, sage ,thyme, celery seed, dried Mexican Oregano, peppermint
	\end{itemize}


\end{itemize}

{\tiny (Ref: ``Harvard Nutritional Psychiatrist Shares the Key Foods for Incredible Mental Health | Dr. Uma Naidoo | Andrew Huberman'' https://www.youtube.com/watch?v=LtHlw7QJT7Y)}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Uma Naidoo}

	\begin{itemize}
\item  Sodium-salt but not in excess, from processed food.
\item  Fast food, like French fries, has sugar (no taste though)
\item  Obsessive Compulsive Disorder (OCD): Avoid MSG (Mono Sodium Glutamate), Parmesan cheese, oyster/tomato sauce
\item  Depression/Anxiety: Mediterranean diet helps: avocado, lean protein, olive oil, seafood, whole grains
\item  Aggression: increases with trans-fats
\item  Have:
	\begin{itemize}

	\item  Pre-biotic: onion, garlic
	\item  Fermented food: Kafir, Kimchi
	\item  Salads: Color of rainbow vegetables (avoid unhealthy toppings), seeds, beans, lemon, herbs
	\end{itemize}

\end{itemize}


{\tiny (Ref: ``Harvard Nutritional Psychiatrist Shares the Key Foods for Incredible Mental Health | Dr. Uma Naidoo | Andrew Huberman'' https://www.youtube.com/watch?v=LtHlw7QJT7Y)}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Andrew Huberman}


	\begin{itemize}
\item  Nervous system functions : Sensation, Perception (spotlight/attention), Feeling, Thoughts, Actions, Triggering immune system
\item  Brain has abstractions of everything around
\item  Abstractions converge at physical phenomenon easily bit also at things like rewards, punishments
\item  Brain outside skull+spinal chord: neural retina, behind eye, not attached to brain. See sunrise and sunset to trigger activities.
\item  Growth Mindset:
	\begin{itemize}
	\item  Dopamine: Pursuit of goal and not much at the achievement of it. Attachment of rewards to efforts
	\item  Serotonin/Oxytocin: Attachment of rewards to goals achievement
	\end{itemize}

\end{itemize}


{\tiny (Ref: ``This Neuroscientist Shows You the Secrets to Obtaining A Growth Mindset | Andrew Huberman'' https://www.youtube.com/watch?v=OGa\_jt3IncY)}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Andrew Huberman}


	\begin{itemize}
\item  Fear: Act in the fearful situation, lateral eye movements are associated with forward-movement, and thus, action.
\item  (my wording) Even if you get external assistance (luck) in your success, you become confident enough to win future battles.
\item  Solution for stress-fear is Forward movement (gets dopamine)
\item  Reward incremental steps, say, run around a block.
\item  Tom Bilyeu: Success is not guaranteed but the struggle is.

\end{itemize}

{\tiny (Ref: ``This Neuroscientist Shows You the Secrets to Obtaining A Growth Mindset | Andrew Huberman'' https://www.youtube.com/watch?v=OGa\_jt3IncY)}


\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Andrew Huberman}


	\begin{itemize}

\item  Hypnosis: relaxing nervous system and opens possibility of nuro plasticity, in contrast, in high alert situation (talking, planing, brain is linear, if then then that). For re-wiring, need deep rest
\item  Deep rest: diaphragmatic breathing, tells brain to be active or rest accordingly (phrenic nerve).
\item  Heightened states of focus by Heavy breathing (Wim Hof), then calm, with double-inhale and long exhale
\item  One change to make: 2-10 minutes of bright light at sunrise
\end{itemize}

{\tiny (Ref: ``This Neuroscientist Shows You the Secrets to Obtaining A Growth Mindset | Andrew Huberman'' https://www.youtube.com/watch?v=OGa\_jt3IncY)}


\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Aaron Alexander}

\begin{itemize}

\item  Theme: Align method (better movements)
\item  Dance (Music + Movement), Pose-stance for better state
\item  Smile (even fake), but if actual and with eyes, changes mood
\item  Exercise: While walking look at others color of eyes. Magic of the moment.
\item  Bring child like aspects: flexibility, directly related to nature, compassion, honesty.
\item  Be more on ground-seated. Look up to trees, Sun, nature. 
\item  Micro-opportunities to do movements, squatting, Walk, 2/3 minutes hang on pull-up bar.
\item  Mind movements: Stillness!! vipassana meditation
\item  Accept yourself. Be better as well. Talk about it.
\end{itemize}

{\tiny (Ref: ``The Real Secret to a Healthy Mind and Body | Aaron Alexander on Health Theory'' https://www.youtube.com/watch?v=YpmfoNTTuNU)}


\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Sam Altman}

\begin{itemize}

\item ``Minimize your own cognitive load from distracting things that don’t really matter. It’s hard to overstate how important this is, and how bad most people are at it.'' (Essay ``The days are long but the decades are short'')
\item ``Sleep seems to be the most important physical factor in productivity for me. Exercise is probably the second most important physical factor. The third area is nutrition.'' (Essay: ``Productivity'')
\end{itemize}

{\tiny (Ref: ``Sam Altman on Choosing Projects, Creating Value, and Finding Purpose'' https://www.youtube.com/watch?v=uEl2KUZ3JWA)}


\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Sam Altman}

\begin{itemize}

\item ``If what you are doing is not important, and if you don’t think it is going to lead to something important, why are you at Bell Labs working on it?’'' (Essay ``You and Your Research by Richard Hamming'')
\item ``Things in life are rarely as risky as they seem. Most people are too risk-averse, and so most advice is biased too much towards conservative paths.'' (Essay: ``The Days Are Long But The Decades Are Short'')
\end{itemize}

{\tiny (Ref: ``Sam Altman on Choosing Projects, Creating Value, and Finding Purpose'' https://www.youtube.com/watch?v=uEl2KUZ3JWA)}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Sam Altman}

\begin{itemize}

\item ``My system has three key pillars: “Make sure to get the important shit done”, “Don’t waste time on stupid shit”, and “make a lot of lists”'' (Essay ``Productivity'')
\item ``He who works with the door open gets all kinds of interruptions, but he also occasionally gets clues as to what the world is and what might be important.'' (Essay: ``You and Your Research by Richard Hamming'')
\end{itemize}

{\tiny (Ref: ``Sam Altman on Choosing Projects, Creating Value, and Finding Purpose'' https://www.youtube.com/watch?v=uEl2KUZ3JWA)}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Sam Altman}

\begin{itemize}

\item ``Our self-worth is so based on our intelligence that we believe it must be singular and not slightly higher than all the other animals on a continuum. Perhaps the AI will feel the same way and note that differences between us and bonobos are barely worth discussing.'' (Essay ``The Merge'')
\item “Surrounding yourself with people that will make you more ambitious”
\item Take time to reflect on your purpose, life and what you are really accomplishing. Ask yourself if you are doing something important or something that matters. It's easy to get caught up in things e.g. office politics, status or power games that don't matter. 
\end{itemize}

{\tiny (Ref: ``Sam Altman on Choosing Projects, Creating Value, and Finding Purpose'' https://www.youtube.com/watch?v=uEl2KUZ3JWA)}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Sam Altman}

\begin{itemize}

\item Take time and explore different things. Learn about different areas. Meet, help and learn from people who are working on different things. Understand that most things won’t work out. 
\item On what to work on: Figuring out what’s working and not after exploring different things. This involves following your intuition, brutal honesty, and focusing on the project that's really working for a sufficient amount of time. Young founders make the mistake of bouncing from projects to projects without giving a project enough time for it to have measurable results. Knowing what to focus on and when to give up are especially hard things to do.  
\end{itemize}

{\tiny (Ref: ``Sam Altman on Choosing Projects, Creating Value, and Finding Purpose'' https://www.youtube.com/watch?v=uEl2KUZ3JWA)}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Sam Altman}

\begin{itemize}

\item  (Not for everyone) Angel investing and poker are great ways to learn about business, psychology and life in general.
\item  Sleep, exercise and nutrition are important for physical productivity. Find out what are your most productive hours of the day and focus on your work don't let others interrupt you during these hours.
\item Shift your perspectives. Look into things from different angles. Surround yourself with people who make you more ambitious.
\end{itemize}

{\tiny (Ref: ``Sam Altman on Choosing Projects, Creating Value, and Finding Purpose'' https://www.youtube.com/watch?v=uEl2KUZ3JWA)}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Sam Altman}

\begin{itemize}

\item Read biographies of people who did amazing things like the Apollo program to motivate yourself and provide you with new perspectives on purpose and risks. 
\item An interesting way to increase your productivity is to have a group of friends who are founders who check in on each other frequently.
\item  Doing anything worthwhile takes a long time and emotional trauma (getting rejected over and over again) and if you aren’t willing to do that you probably won’t succeed. 
\end{itemize}

{\tiny (Ref: ``Sam Altman on Choosing Projects, Creating Value, and Finding Purpose'' https://www.youtube.com/watch?v=uEl2KUZ3JWA)}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Sam Altman}

Some notes on the deferred life plan:

\begin{itemize}

\item One of the problems with the deferred life plan is that these people are usually not that committed to the plan in the first place. E.g. if you want to go build a rocket, just go build a rocket. You can’t say you are going to do something like ‘I am going to build a \$100 million crypto fund before I start my rocket company.’ Usually, this person doesn’t build either of these ventures. 
\item Another problem with the deferred life plan is that people like investors and employees can sense that you aren’t authentic or committed to the vision of the company, so you probably won’t win their support.
\end{itemize}

{\tiny (Ref: ``Sam Altman on Choosing Projects, Creating Value, and Finding Purpose'' https://www.youtube.com/watch?v=uEl2KUZ3JWA)}
\end{frame}

