%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Jottings from Talks, Articles}

{\small Nassim Taleb}


\end{center}
\end{frame}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\large Skin in the Game}

{\small Talk at Google}


\end{center}
\end{frame}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Expert Problem}

\begin{itemize}
\item Who, in your field, recognizes you? your peers or the client? If peers, then its Expert Problem.
\item Who recognizes actors? the Film-fare awards (ppl from same fraternity), then not good? but if it goes well on Box office, then the client/public approval, is supreme.
\item (yk): In company, who decides you are better than your neighbor? you peers/boss, then not good. If appreciated by client, who pays you, then its good.
The One who pays, his/her opinion matters.
\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Hammurabi's code}

\begin{itemize}
\item If building collapses, then the architect needs to be given death punishment.
\item Its not just the symmetry or  tit-for-tat balancing principal, but a risk assignment principal.
\item If you have created risk for others, you OWN it.

\item That's ``skin in the game''.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Asymmetries}

\begin{itemize}
\item ``If you do not lose from the losses of a business, you shall not gain from the gains of it''
\item There is an asymmetry in rewards in the scenarios of losses and gains.
\item Do decision makers, politicians, armchair intellectuals suffer, if their decisions cause, wars/riots.
\item Unless you yourself suffer from your own decisions, your skin is not in the game.
\item Need to take that RISK, of being exposed to results of your decisions.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Risk as Virtue}

\begin{itemize}
\item If you don't suffer yourself, you can not be the Christ. Thats where respect comes.
\item If you don't bet your life, like Socrates, for your ideas, you don't earn the respect.
\item Journalists covering stories in dangerous situations.
\end{itemize}
\end{frame}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Inequality}

\begin{itemize}
\item Static (does not change) and dynamic (changes over time)
\item Static: the same top 50 families have been the richest since the last 500 years
\item Dynamic: The rich and the poor are taking turns. Getting swapped.
\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Green Lumber Fallacy}

\begin{itemize}
\item How much ever research you do from outside, that wont be enough.
\item To play the game to know it from the inside instead of reading/researching about it. 
\item One sees things differently from the inside.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Lindy Effect}

\begin{itemize}
\item Ideas which have stood test of time, will continue to do so.
\item Older things in the intellectual domain, which are non-perishable such as books, ideas are likely to outlive newer ideas and books
\item For perishable objects, the less likely it is for the old to outlive the new. \item For example, a 90-year-old human being is less likely to outlive a 40 old-year-old human being.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Minority Rule}

\begin{itemize}
\item The ones who are crazy enough to think they can change the world, are the ones who do
\item The ones who challenged the status quo and were unwilling to give up or compromise, brought us freedom from the colonial rules, brought us innovation and have changed the world.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{References}
\begin{itemize}
\item Lessons from Fireside chat by Nassim Nicholas Taleb and Naval Ravikant
- Ravi Ranjan
\end{itemize}
\end{frame}