\section{Key Habits}
\begin{itemize}[noitemsep,nolistsep]
\item Leo Babauta
	\begin{itemize}[noitemsep,nolistsep]
	\item Set your 3 MITs (Most Imprtant Tasks) each morning
	\item Single Task - focus your attention
	\item Zero Inbox (Work In Progress mails ok)
	\item Work while disconnected
	\item Keep your desk de-cluttered
	\item Stick to 5 sentences emails (make words powerful)
	\item Say NO to any commitment outside your goals
	\item Low information diet: emails + twice a day, 
	\end{itemize}

\item Your Job is to Make Art - Seth Godin at ConvertKit Craft & Commerce 2017
 	\begin{itemize}[noitemsep,nolistsep]
	\item Dont go for mass market, margins are thin, need to make compromises, average quality, more marketing needed
	\item Go for small-niche market enough to sustain you. If you are solving their real need, they themselves will advertize and you will grow.
	\item Do Remarkable (and not what everybody else does), it should be worth making remark about.
	\item Don't be average!! Need edge cases.
	\item Dont be copy-cat, its not worth the effort. Even if scale helps, you become in price-race. Thats different than leverage though. 
	\item Your Special Knowledge or product should not be copy-able. Thats personal brand. You own it and are accountable for it.
	\end{itemize}
\item Gut Health - Ben Warren's top 10 tips for a healthy gut.
	\begin{itemize}[noitemsep,nolistsep]
	\item Food/dairy intolerance causing Back pain, difficultly nose breathing, 
	\item IGG IGE test for whey protein, lactose/milk intolerance
	\item Most of the immune system is in stomoch as it has to prottect from outside food.
	\item It decides which protein to keep (food) and which to destroy (virus/bacteria are proteins too!!)
	\item Gluten in some folks gets identified as virus and immune reactions happen.
	\item Leaky gut affects body
	\item Auto immune: immune system goes hyper and attacks good parts of internal body
	\item Gut-brain axis : 3 way intersection of brain, gut and microbiome.
	\item For digestion, mental relaxation is needed. Control breathing, diaphragmatic, while eating.
	\item Chew food to liquid
	\item Apple cider before meal (if there isn't strong acid, this will help. If you already have it, then you can stop and take bicarbonate soda) same in case acid reflux.
	\item Start day with warm water + lemon. Gets stomach ready for the day
	\item If at all you need dairy products, take as raw as possible. Avoid if possible.
	\item Gluten (wheat, maida, etc) and Lactose (dairy) are to be avoided.
	\item Eat fermented food daily, probiotic
	\end{itemize}
	
\item Chris Bailey
	\begin{itemize}[noitemsep,nolistsep]
	\item Schedule time to completely disconnect from work
	\item Use visualizations to become more productive
	\item Capture all of the open loops in your head
	\item When you meet someone, shut off phone completely
	\end{itemize}

\item Avinash Dharmadhikari
	\begin{itemize}[noitemsep,nolistsep]
	\item Know thy-self - Ongoing
	\item Chose career of favorite topic - CAD
	\item Excellence and Creativity in the chosen topic
	\item \foreignlanguage{sanskrit}{विषय कळलेला पाहिजे ज्ञानावर पकड}. 
	\item Yog \foreignlanguage{sanskrit}{आसने, सूर्यनमस्कार, प्राणायाम, ध्यान}
	\item \foreignlanguage{sanskrit}{स्वाधाय : कोणताही विषय समोर आला तरी त्याचा अभ्यास करण्याचे कौशल्य}. Notes, Ref Cards
	\item Good command over English, Bilungual, Finance.
	\item Awareness of latest trends of your work.
	\item Entrepreneur in my field.  Teacher prepares students
	\item Creator of wealth (value addition to the topic)  
	\item \foreignlanguage{sanskrit}{वैश्विकता}: Do things at par with global standards
	\end{itemize}

\item The book of YOGA - Christina Brown
	\begin{itemize}[noitemsep,nolistsep]
	\item Yoga is a state of mind. Stillness fosters awareness.
	\item Physical exercises still the body. Breath to focus the mind
	\item Relaxation to quieten the body and mind
	\item Chanting to arouse and then calm emotions
	\item Meditation to center the spirits.
	\item Yoga postures bring strength to the weak areas and soften the tight spots.
	\item अभ्यास : Repeated study/effort, then becomes effortless
	\item  आसन builds and controls प्राण  - the vital force
	\item Mind is the master of senses and the breath is the master of the Mind.
	\item When the breath flows steadily your आसन becomes closer to perfect
	\item Frequently check your breathing
	\item Finding the quietness that lies within yourself
	\item Push your boundaries every time. Don't overdo it.
	\item यम : Compassion for all beings. अहिंसा (tolerance, kindness), सत्य, अस्तेय (stealing), ब्रह्मचर्य (moderation) अपरिग्रह (non-accumulation, simplicity)
	\item नियम : शौच (purity), संतोष (contentment), तप (dedication/fire-determiniation), स्वाध्याय, ईश्वर-प्रणिधान
	\item आसन  (postures)
	\item प्राणायाम (breath control)
	\item  प्रत्याहार (withdrawal of senses)
	\item धारणा (concentration, mindfulness, paying attention)
	\item ध्यान (meditation)
	\item समाधी
	\item Start and End any activity with relaxation
	\item Let it go, detachment. Tense and then relax parts one by one.
	\item Stay Still and Don't worry
	\end{itemize}
\item Blog Maria Popova
	\begin{itemize}[noitemsep,nolistsep]
	\item  The secret of happiness: ``Find something more important than you are'' - philosopher Dan Dennett
	\item Don't go after prestigious positions, HoD, on committees etc. Waste of time.
	\item Steve Jobs:  And the only way to do great work is to love, what you do. If you haven't found it yet, keep looking. Don't settle
	\item The whole future lies in uncertainty: live immediately.
	\item No activity can be successfully pursued by an individual who is preoccupied 
	\item 7 Learnings:
		\begin{itemize}[noitemsep,nolistsep]
		\item Allow yourself the uncomfortable luxury of changing your mind.
		\item Do nothing for prestige or status or money or approval alone. Have goal more than the promotion!!
		\item Be generous. With your time.
		\item Build pockets of stillness into your life. Sleep.
		\item Don't believe what others say about you
		\item Presence is far more intricate and rewarding an art than productivity.
		\item Expect anything worthwhile to take a long time
		\end{itemize}
	\end{itemize}
\end{itemize}
