\begin{frame}[fragile]
\frametitle{Ch 1 : De-cluttering}
\begin{itemize}
\item If you haven't used it in the last year, junk it
\item Have To-Do lists based on context, like @Home, @Work, @Calls etc
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 2 : Single Tasking}
\begin{itemize}
\item multi-tasking is less efficient
\item Tasks inbox @
\item Google Tasks-Calendar
\item Emails - Outlook, Yahoo, Gmail
\item Diary (short term)
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 3 : Edit your commitments}
\begin{itemize}
\item For each area their could be goals
\item Just keep 2-3 goals
\item Relax-Fun
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 4 : Eliminate all but the essential}
\begin{itemize}
\item Reduce most of the inputs
\item No TV, sites you visit, Newspapers, Magazins, RSS feeds, Blogs
\item Deactivate useless accounts
\item Do minimum but quality work
\item it should be contrararian to stand out
\item Don't spread too thin
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 5. Don't do everything on your task list, you will never get it to zero, its ok!!}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 6. Art of Doing nothing}
\begin{itemize}
\item Close all distractions - mobile, TV, Computer etc
\item Sit quietly - do attentive breathing
\item If you are waiting for something, in queue, do nothing, no emails, no reading, just focus on breathing
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 7. Declutter your mind}
\begin{itemize}
\item Write down everything that you have on mind, on paper, later either take it to tasks or mms
\item Office: Keep diary-journal, for Personal, keep small diary for daily noting
\item Just do less tasks - do the ones you take very nicely, then relax/enjoy
\item Let GO - frustrations, worries, grudges
\item Slow down - walking, talking, working : NO RUSH
\item Get load off to someone - delegate - set expectations
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 8. Simplicity Tips}
\begin{itemize}
\item Get rid off non essential commitments
\item Get rid of non essential items - books, cassettes, CDs, electronics, clothes, e-accounts, blogs, newsletters, rss feeds, bookmarks etc stuff
\item Limit your communication - close IM, digital detox
\item Keep Work files on Work Laptop only, keep personal files on Home Laptop, no mix-up
\item Read all the unread books, make MMs
\item Watch all unseen CDs, HDD movies on Sundays
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 9. Eat Slower}
\begin{itemize}
\item Don't read newspaper or watch anything
\item SLOW (not FAST) food movement
\item Pay attention to what you are eating, taste it
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 10. Purpose your day}
\begin{itemize}
\item 3 MITs. first has to be first one in the morning, may be health related activities
\item Closely understand your work, talk to people
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 11. Focus on big rocks}
\begin{itemize}
\item Weekly tasks to accomplish
\item Put them on Google tasks as well as white board
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 12: Clear-out Inbox}
\begin{itemize}
\item Junk => Delete
\item Long one/Info => move to appropriate folder as unread
\item If quick => reply back with 4-5 lines
\item Waiting for response today => Keep them in Inbox
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 13. Clear your Desk}
\begin{itemize}
\item Keep essential items only
\item Keep work-personal phone pdf handy
\item Keep ready refs, imp mm pdfs, accounts-password pdf handy
\item Keep backup of all on Google docs as well as printed set at home and office folder
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 14. Become an early riser}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 15. Be motivated when you are in slump}
\begin{itemize}
\item Create Goals mm with pictures and paste it on wall
\item Publicize goals to public?
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 16. Make most of your laziest day}
\begin{itemize}
\item Relax, take nap, go for a walk
\item Sunday
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 17. Decompress after high stress}
\begin{itemize}
\item Deep breathing
\item Self Massage
\item Take a walk
\item Take a day off, don't do anything, yes - anything
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 18. Cultivate compassion in your life - be kind}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 19. Escape Materialism}
\begin{itemize}
\item Donate all un-necessary items
\item Keep minimum-quality ones
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 20. Practical tips for living with a golden rule}
\begin{itemize}
\item treat others the way you want to get treated
\item be helpful, kind and friendly
\item STOP CRITICISM
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 21. Accept criticism with grace and appreciation}
\begin{itemize}
\item try to explain your stance to give clarity
\item "I dont think I made myself very clear..."
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 22. Have faith in humanity and restore kindness}
\begin{itemize}
\item people are not meeting much
\item becoming rude, lonely
\item Practice kindness, help others without expecting anyting in return
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 23. Boost your self confidence}
\begin{itemize}
\item Groom yourself
\item good language
\item good looks
\item good dressing
\item Know yourself
\item start looking at your thoughts - which are predominant ones
\item are you always fault finding?
\item what are my limitations, fears?
\item Speak slowly
\item Stand talll and smile
\item Increase competence
\item Volunteer
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Ch 24. Live your life consciously}
\begin{itemize}
\item Have clarity on what you are doing and for what?
\item Take control of your life
\item Consider your impact on world
\item Write best books, may be free e-books
\item Write best apps and give them free/nominal charge
\item Give project/thesis guidance - free
\item Build leaders, teams
\end{itemize}
\end{frame}
