%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Introduction to Mental Models}
  \begin{itemize}
    \item Mental models are frameworks to simplify complex decision-making.
    \item Popularized by Charlie Munger and Shane Parrish.
    \item Originates from cognitive psychology and systems theory.
    \item Helps in investing (e.g., Munger's latticework), policymaking, and life choices.
    \item E.g., Ratan Tata applying mental models in Tata Nano's design.
    \item Be aware of over-relying on one model; use a toolbox approach.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{First Principles Thinking}
  \begin{itemize}
    \item Break problems down to their fundamental truths.
    \item Originates from Aristotle and physics.
    \item Used in startups, e.g., Ola dissecting cab logistics vs. copying taxi systems.
    \item In cooking, understanding base ingredients vs. recipes.
    \item E.g., ISRO's cost-effective Mars mission using fundamental physics and constraints.
    \item Beware of ignoring proven heuristics and reinventing unnecessarily.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Inversion}
  \begin{itemize}
    \item Thinking in reverse , ``what would cause failure?''
    \item Inspired by Carl Jacobi's ``invert, always invert.''
    \item In finance: prevent loss before seeking gain.
    \item In daily life: avoiding bad health rather than only pursuing good.
    \item E.g., B-schools teaching case studies of failed Indian startups.
    \item Avoid over-focusing on negatives; it's a tool, not a worldview.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Opportunity Cost}
  \begin{itemize}
    \item Cost of the next best alternative foregone.
    \item Core principle in economics since classical era.
    \item Choosing civil services over entrepreneurship , missed upside.
    \item In Indian agriculture: water for paddy vs. cash crops.
    \item E.g., investor choosing fixed deposit vs. equity.
    \item Don't ignore hidden or non-financial costs; measure holistically.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Second-Order Thinking}
  \begin{itemize}
    \item Anticipating consequences of consequences.
    \item Key to systems thinking; used by top strategists.
    \item In politics: free electricity → higher consumption → grid stress.
    \item In business: discounts → loss leaders → brand erosion.
    \item E.g., UPI adoption → cashless economy → surveillance concerns.
    \item Avoid paralysis by analysis; balance depth with action.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{The Map is Not the Territory}
  \begin{itemize}
    \item Models are simplifications , not reality itself.
    \item Coined by Alfred Korzybski, popular in systems science.
    \item GDP $\neq$ actual prosperity; rankings $\neq$ real competence.
    \item E.g., exam scores $\neq$ intelligence; IRCTC waitlist $\neq$ travel reality.
    \item E.g., BPL card $\neq$ real poverty in rural India.
    \item Don't confuse labels or proxies with full understanding.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Circle of Competence}
  \begin{itemize}
    \item Know what you know , and what you don't.
    \item Warren Buffett's key idea; deeply tied to humility.
    \item Investors stick to known sectors , pharma vs. tech.
    \item E.g., Indian cricket team sticking to seamers on green pitches.
    \item E.g., Byju's scaling fast in edtech, failed in physical schools.
    \item Don't make your circle too small , be open to learning.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Ockham's Razor}
  \begin{itemize}
    \item Simplest explanation is often correct.
    \item Named after William of Ockham, 14th century.
    \item Used in diagnosis, journalism, and science.
    \item E.g., missing train due to traffic vs. conspiracy by cabbie.
    \item E.g., Aadhaar leaks more likely due to mismanagement than espionage.
    \item Beware of oversimplification; simple $\neq$ accurate.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{The Lindy Effect}
  \begin{itemize}
    \item The longer something survives, the longer it's likely to.
    \item Popularized by Nassim Taleb; derived from theater.
    \item Sanskrit, Ayurveda , resilient knowledge in Indian context.
    \item Brands like Amul, Tata indicate trust through time.
    \item E.g., epics like Mahabharata enduring cultural relevance.
    \item New $\neq$ better; but old $\neq$ always useful , evaluate critically.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Sunk Cost Fallacy}
  \begin{itemize}
    \item Continuing due to past investment, not future value.
    \item Studied in behavioral economics.
    \item Government projects continued despite low returns.
    \item E.g., B-school student finishing MBA despite hating it.
    \item E.g., personal relationships carried forward ``because of time invested.''
    \item Don't throw good money (or time) after bad.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{The Pareto Principle (80/20 Rule)}
  \begin{itemize}
    \item 80% of results come from 20% of efforts.
    \item Discovered by Vilfredo Pareto in economics.
    \item E.g., 20% of customers bring 80% revenue , common in Indian retail.
    \item In exams, 20% topics cover 80% questions.
    \item E.g., Indian IT firms rely heavily on top 20% of clients.
    \item Avoid ignoring the remaining 80% entirely , edge cases matter.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Cognitive Biases}
  \begin{itemize}
    \item Systematic deviations from rational thinking.
    \item Studied extensively by Kahneman and Tversky.
    \item Media bias, confirmation bias, anchoring , common in investing and politics.
    \item E.g., brand loyalty despite better alternatives.
    \item Indian voters influenced by recency bias during elections.
    \item Learn biases to spot them, not to feel superior.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Probabilistic Thinking}
  \begin{itemize}
    \item Thinking in terms of likelihoods, not certainties.
    \item Core to Bayesian reasoning and decision theory.
    \item E.g., cricket match predictions, monsoon forecasts.
    \item Stock investors use expected value calculations.
    \item E.g., Indian RTOs plan road design using accident probabilities.
    \item Avoid overconfidence; even 90% odds fail 1 in 10 times.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{The Dunning-Kruger Effect}
  \begin{itemize}
    \item Incompetent people overestimate their competence.
    \item Coined by psychologists Dunning and Kruger.
    \item E.g., novice trader in India believing they're stock experts post one gain.
    \item Political debates full of loud but uninformed opinions.
    \item E.g., early success of startups can lead to overexpansion.
    \item Competence includes knowing limits; humility is key.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Hanlon's Razor}
  \begin{itemize}
    \item Never attribute to malice what can be explained by stupidity.
    \item Popular in management and conflict resolution.
    \item E.g., government inefficiency $\neq$ conspiracy.
    \item Indian Railways delays often due to process, not sabotage.
    \item In family arguments, ignorance may explain behavior better than bad intent.
    \item Beware of excusing true malice , discern with care.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Systems Thinking}
  \begin{itemize}
    \item Viewing elements as parts of interrelated wholes.
    \item Rooted in cybernetics and ecology.
    \item E.g., Indian river pollution due to upstream waste + politics + habits.
    \item Public health influenced by education, nutrition, and social norms.
    \item E.g., traffic = vehicles + roads + behavior + enforcement.
    \item Risk: complexity can obscure actionable insight , avoid analysis paralysis.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{The Availability Heuristic}
  \begin{itemize}
    \item People judge likelihood by what comes easily to mind.
    \item From cognitive psychology.
    \item After plane crash news, people avoid flying.
    \item E.g., fear of crime rising due to sensational Indian news channels.
    \item COVID panic in India driven by social media images.
    \item Recognize bias: what's vivid $\neq$ what's common.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Skin in the Game}
  \begin{itemize}
    \item Decision-makers must share risks of their actions.
    \item Advocated by Nassim Taleb.
    \item E.g., Indian politicians rarely affected by laws they make.
    \item Business owners risking personal capital vs. salaried CEOs.
    \item E.g., doctors prescribing tests vs. family treating conservatively.
    \item Don't assume skin always = alignment; people may still act irrationally.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Confirmation Bias}
  \begin{itemize}
    \item Tendency to seek info that confirms preconceptions.
    \item Found in psychology and behavioral economics.
    \item E.g., political debates in India , media consumed selectively.
    \item Investors seek news that supports their portfolio.
    \item E.g., religious or caste-based beliefs reinforced via social networks.
    \item Actively seek disconfirming evidence for better clarity.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{The Law of Diminishing Returns}
  \begin{itemize}
    \item Each additional input yields less output after a point.
    \item Core to economics and productivity.
    \item E.g., studying 10 hrs vs. 20 hrs doesn't double marks.
    \item Government subsidies show lower impact over time.
    \item E.g., fertilizer overuse harming Indian soils.
    \item Be aware of optimal input level , don't push endlessly.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Falsifiability}
  \begin{itemize}
    \item A theory must be testable to be scientific.
    \item Philosopher Karl Popper's key principle.
    \item E.g., Astrology in India: not falsifiable = pseudoscience.
    \item Good economic models are those we can disprove.
    \item E.g., ISRO missions are evaluated on clear success/failure.
    \item Avoid vague goals or models that can't fail , they're useless.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Survivorship Bias}
  \begin{itemize}
    \item Focus on successes and ignore failures.
    \item WWII bomber example; key in statistics.
    \item E.g., highlighting startup unicorns, ignoring 90% failures in India.
    \item Bollywood stories of actors from small towns miss thousands who failed.
    \item E.g., glorifying IIT success without showing coaching burnout cases.
    \item Always ask: ``What am I not seeing?''
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{The Peter Principle}
  \begin{itemize}
    \item People get promoted to their level of incompetence.
    \item Formulated by Laurence J. Peter.
    \item Seen in bureaucracies and Indian PSUs.
    \item E.g., great engineer made manager , fails at leadership.
    \item Indian government often promotes seniority, not ability.
    \item Avoid automatic promotions , match role to strengths.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Tragedy of the Commons}
  \begin{itemize}
    \item Individuals overuse shared resources for personal gain.
    \item Coined by Garrett Hardin, 1968.
    \item E.g., overgrazing in Indian village pastures.
    \item Overfishing in coastal India, water tanker usage in Bangalore.
    \item Pollution of Yamuna due to collective neglect.
    \item Collective solutions + incentives required to escape the trap.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Reciprocity}
  \begin{itemize}
    \item People respond to kindness with kindness.
    \item From social psychology, basis of social contracts.
    \item E.g., Indian wedding invites → social obligation to reciprocate.
    \item Business offers: ``free'' samples → expectation to buy.
    \item Indian politics: favors given in return for votes.
    \item Can be manipulated , be conscious of emotional traps.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Thought Experiment}
  \begin{itemize}
    \item Imagining a scenario to reason abstractly.
    \item Used by Einstein, Schrödinger, philosophers.
    \item E.g., ``What if no one followed traffic signals in Delhi?''
    \item Indian planners simulate monsoon scenarios for disaster prep.
    \item Business leaders imagining customer journeys to refine UX.
    \item Avoid mental experiments with flawed premises.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Relativity}
  \begin{itemize}
    \item Perception depends on comparison.
    \item Not just physics , applies in psychology and economics.
    \item E.g., Rs.1000 seems big at a tea shop, small at Croma.
    \item Discounted MRPs manipulate perception of value.
    \item E.g., coaching institutes: ``Only Rs.1 lakh'' vs. ``Just 2 months' salary.''
    \item Avoid judging in isolation; watch your frame of reference.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Thermodynamics}
  \begin{itemize}
    \item Energy systems tend toward disorder (entropy).
    \item From physics; metaphor in organizational design.
    \item E.g., Indian government departments decay without active effort.
    \item Relationships degrade without energy (attention, care).
    \item E.g., neglected public infrastructure like Indian toilets, libraries.
    \item Systems must be fed with effort to counter entropy.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Inertia}
  \begin{itemize}
    \item Objects at rest stay at rest; systems resist change.
    \item From Newtonian physics; metaphor for habits, culture.
    \item Bureaucracies in India resist reform , status quo bias.
    \item People stick to routines despite better alternatives.
    \item E.g., cash use persists despite UPI in rural India.
    \item Momentum can be good or bad , be mindful of direction.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Friction and Viscosity}
  \begin{itemize}
    \item Resistance slows systems down.
    \item Physics origin, applied in design thinking.
    \item E.g., paperwork in Indian passport process adds friction.
    \item Online education failing due to tech/infrastructure drag.
    \item E.g., MSME loans delayed by regulatory viscosity.
    \item Reduce friction strategically, but preserve checks where needed.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Velocity}
  \begin{itemize}
    \item Speed in a particular direction.
    \item Physics model applied to business and policy.
    \item E.g., Indian startup growth = velocity, not just speed.
    \item Quick reforms + right direction = compounding effect.
    \item E.g., GST rollout aimed to increase fiscal velocity.
    \item Beware of high speed in wrong direction , causes more harm.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Leverage}
  \begin{itemize}
    \item Small inputs yielding large outputs.
    \item Originates from mechanics and finance.
    \item E.g., using tech (like UPI) to scale access to banking.
    \item Influencers use platforms to gain massive reach.
    \item Debt in real estate , high leverage in Indian housing boom.
    \item Use leverage carefully; too much can break the system.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Activation Energy}
  \begin{itemize}
    \item Minimum energy required to start a reaction.
    \item Chemistry origin; metaphor for habits and change.
    \item E.g., initial setup of solar in Indian homes is high, then payoff.
    \item Form-filling keeps citizens from accessing subsidies.
    \item E.g., waking up early needs energy ``spike'' at first.
    \item Lowering activation energy = increasing adoption.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Catalysts}
  \begin{itemize}
    \item Something that accelerates change without being consumed.
    \item From chemistry; used in transformation processes.
    \item E.g., a good mentor can catalyze career in Indian startups.
    \item Policies like Make in India as industrial catalysts.
    \item E.g., cricket coach who turns underdog into star.
    \item Catalysts don't guarantee success , they enable it.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Alloying}
  \begin{itemize}
    \item Combining elements for strength.
    \item From metallurgy; used metaphorically in teams/ideas.
    \item E.g., diverse coalition governments in India.
    \item Interdisciplinary education = alloy of skills.
    \item E.g., Hindi + tech = strong vernacular apps.
    \item Alloys may have trade-offs , balance strength vs. flexibility.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Evolution - Natural Selection}
  \begin{itemize}
    \item Survival of the fittest over generations.
    \item Darwinian principle; applicable to markets.
    \item Indian startups that adapt thrive (Zerodha, Paytm).
    \item Weak policies die out over time; strong ones stay.
    \item E.g., traditional farming surviving despite modern competition.
    \item Avoid romanticizing all survivors , some survive by chance.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Evolution - Adaptation}
  \begin{itemize}
    \item Organisms change to fit environment.
    \item Evolutionary biology principle.
    \item E.g., Indian retail moving from cash to QR codes.
    \item COVID forced remote working and online schooling.
    \item Small businesses adopted e-commerce or died.
    \item Adaptation is not always optimal , may be reactive.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Ecosystems}
  \begin{itemize}
    \item Interdependent networks of entities.
    \item From ecology; applied to business, tech.
    \item E.g., India's startup ecosystem: VCs, colleges, infra.
    \item Agriculture involves weather, soil, politics, supply chain.
    \item Bollywood = actors + OTT + media + fans.
    \item Don't isolate systems , analyze interactions.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Niches}
  \begin{itemize}
    \item Specialized roles within systems.
    \item From biology, used in marketing and strategy.
    \item E.g., Indian vernacular YouTubers targeting Tier-2 cities.
    \item Brands like Patanjali tapping Ayurvedic niche.
    \item Job roles like drone pilot, data annotator = new niches.
    \item Niches can be fragile , depend on broader system health.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Self-Preservation}
  \begin{itemize}
    \item Tendency of organisms/systems to protect themselves.
    \item Evolutionary instinct; metaphor in institutions.
    \item E.g., Indian babus resisting administrative reforms.
    \item People resist feedback that threatens ego.
    \item E.g., companies killing innovations to protect core business.
    \item Self-preservation is natural, but can block growth.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Replication}
  \begin{itemize}
    \item Ability to copy and scale reliably.
    \item From biology and manufacturing.
    \item E.g., Indian franchise model , CCD, Amul parlors.
    \item Education: coaching classes cloned in every city.
    \item E.g., political strategies replicated across states.
    \item Mindless replication can ignore local context.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Cooperation}
  \begin{itemize}
    \item Working together for mutual benefit.
    \item Core to human evolution and society.
    \item SHGs in India empowering rural women.
    \item Farmers pooling land/machinery.
    \item Swachh Bharat relied on mass cooperation.
    \item Needs trust, alignment , forced cooperation fails.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Hierarchical Organization}
  \begin{itemize}
    \item Systems structured in layers of control.
    \item Found in biology, military, governance.
    \item E.g., Indian bureaucracy: central, state, district levels.
    \item Companies with vertical vs. flat hierarchies.
    \item Indian family structures: elders → juniors.
    \item Hierarchy brings order, but can stifle speed and creativity.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Incentives}
  \begin{itemize}
    \item Behavior is shaped by rewards and penalties.
    \item Economics principle; vital in policy and business.
    \item E.g., LPG subsidy linked to Aadhaar = better targeting.
    \item Swiggy/Zomato drivers incentivized on deliveries.
    \item Voters swayed by freebie promises.
    \item Misaligned incentives = corruption, manipulation.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Tendency to Minimize Energy}
  \begin{itemize}
    \item Systems prefer the path of least resistance.
    \item Physics + human psychology.
    \item E.g., people choose WhatsApp forwards over research.
    \item Politicians use slogans instead of nuanced solutions.
    \item E.g., shortcuts in JEE prep , coaching hacks.
    \item Shortcuts are tempting , but costly if misused.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Feedback Loops}
  \begin{itemize}
    \item Outputs become new inputs, amplifying or correcting.
    \item From cybernetics; applies in economics, learning.
    \item E.g., social media likes → more posts → more likes.
    \item UPI usage loop: adoption → trust → more users.
    \item Crime in areas → police presence → less crime.
    \item Watch for both positive (amplifying) and negative (balancing) loops.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Closure}
  \begin{itemize}
    \item Desire for resolution or finality.
    \item From Gestalt psychology.
    \item E.g., Indians rushing to conclusions in legal cases.
    \item Political narratives simplify messy realities.
    \item Gossip fills gaps in incomplete news stories.
    \item Don't force closure , embrace uncertainty when necessary.
  \end{itemize}
\end{frame}