\section{Background}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Background}
\begin{center}
{\Large Effective Altruism: Core Ideas}
\end{center}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{What is Effective Altruism?}
  \begin{itemize}
    \item Effective Altruism (EA): using evidence and reason to find the most pressing problems and most effective solutions, then acting on them.
    \item Some interventions are 100–1000x more effective than others; careful choices massively increase impact.
    \item Core principles: 
      \begin{itemize}
        \item Scope sensitivity – help more when possible
        \item Impartiality – value all lives equally
        \item Scout mindset – seek truth, update beliefs
        \item Recognition of tradeoffs – every choice has opportunity costs
      \end{itemize}
    \item EA originated at Oxford, now a global community across 70+ countries.
    \item Anyone applying these principles—whether through careers, donations, or advocacy—is part of EA.
  \end{itemize}
  
{\tiny (Ref: https://www.effectivealtruism.org/articles/introduction-to-effective-altruism)}  	  
  
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Pressing Problems \& How to Act}
  \begin{itemize}
    \item \textbf{Global Health \& Poverty:} 700m live on <$1.90/day. Bednets save lives at $\sim\$$5,500 per life vs. $1m+ in rich countries. GiveWell charities have saved 150k+ lives.
    \item \textbf{Pandemics:} COVID killed 21m; future outbreaks could be worse. Yet prevention receives a fraction of counterterrorism funding. EA funds research, policy, rapid trials.
    \item \textbf{AI Safety:} Advanced AI could bring abundance or existential risk. Alignment research ensures AI furthers human values, but researchers are vastly outnumbered by capability builders.
    \item \textbf{Animal Welfare:} 10bn animals suffer in factory farms yearly. EA supports corporate campaigns, advocacy, and alternative proteins to reduce suffering.
    \item \textbf{Better Decision-Making:} Forecasting, prioritization research (e.g. Metaculus, Global Priorities Institute) strengthen society’s ability to handle global challenges.
    \item \textbf{Taking Action:} 
      \begin{itemize}
        \item High-impact careers (80,000 Hours)
        \item Donate effectively (GiveWell, Giving What We Can)
        \item Found/join orgs tackling neglected issues
        \item Build communities and advocate for systemic change
      \end{itemize}
    \item Even modest contributions, if well directed, can save many lives or reduce existential risks.
  \end{itemize}
  
{\tiny (Ref: https://www.effectivealtruism.org/articles/introduction-to-effective-altruism)}  	  
  
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Core Principles of Effective Altruism}
  \begin{itemize}
    \item \textbf{Scope sensitivity}: prioritize saving more lives over fewer
    \item \textbf{Impartiality}: help those most in need, regardless of distance or similarity
    \item \textbf{Scout mindset}: seek truth, avoid bias, update beliefs
    \item \textbf{Recognition of tradeoffs}: limited time and money require prioritization
    \item \textbf{Expected value}: judge actions by expected impact, not certainty
    \item \textbf{Thinking on the margin}: maximize benefit of each extra resource
    \item \textbf{Consequentialism}: focus on outcomes while avoiding “ends justify means”
    \item \textbf{Openness to unusual ideas}: remain receptive as history shows consensus can be wrong
    \item \textbf{INT framework}: prioritize problems that are important, neglected, and tractable
    \item \textbf{Crucial considerations}: seek insights that could radically change strategy
    \item \textbf{Forecasting}: make predictions explicit and learn from errors
    \item \textbf{Fermi estimates}: rough calculations to compare options by expected value
  \end{itemize}
  
{\tiny (Ref: https://www.centreforeffectivealtruism.org/core-principles)}  	  
  
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Taking Action Effectively}
  \begin{itemize}
    \item Choose high-impact careers (e.g., with guidance from 80,000 Hours)
    \item Donate to rigorously vetted charities (e.g., GiveWell, Giving What We Can)
    \item Found or support organizations tackling urgent global problems
    \item Build and grow communities focused on solving pressing challenges
    \item Apply EA principles in any domain of life, at any scale
    \item Even modest, well-directed contributions can save many lives
    \item Collective action amplifies individual impact on humanity’s biggest issues
  \end{itemize}
  
  
\end{frame}



\section{Frameworks \& Methodologies}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Frameworks and Methodologies}
      \begin{itemize}
        \item Importance–Neglectedness–Tractability (INT) framework for cause selection
        \item Crucial considerations: one overlooked factor can flip an intervention’s value
        \item Forecasting: make explicit predictions to learn and improve decisions
        \item Fermi estimates: rough calculations highlight key uncertainties and tradeoffs
        \item Tools are provisional, requiring ongoing refinement
      \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Disagreements in Effective Altruism}
      \begin{itemize}
        \item EA community does not agree on all priorities
        \item Differences arise from varying values and moral perspectives
        \item Methodological disagreements also shape choices
        \item Disagreements can be substantial and influence cause selection
        \item Shared principles provide unity despite divergent conclusions
      \end{itemize}
\end{frame}
\section{Day 1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Day 1}
\begin{center}
{\Large Day 1: [Placeholder]}
\end{center}
\end{frame}

\section{Day 2}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Day 2}
\begin{center}
{\Large Day 2: [Placeholder]}
\end{center}
\end{frame}

\section{Day 3}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Day 3}
\begin{center}
{\Large Day 3: [Placeholder]}
\end{center}
\end{frame}

\section{Day 4}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Day 4}
\begin{center}
{\Large Day 4: [Placeholder]}
\end{center}
\end{frame}

\section{References}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{References}
  \begin{itemize}
    \item The Introduction to Effective Altruism Handbook https://forum.effectivealtruism.org/handbook
	\item EA Resources https://www.effectivealtruism.org/resources
	\item EA Introduction https://80000hours.org/podcast/effective-altruism-an-introduction/
  \end{itemize}

\end{frame}