%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Jottings from Talks, Tweets}

{\small Naval Ravikant}


\end{center}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Goals vs Being Present}

\begin{itemize}
\item Goals: living in future, obligations, urge to do more and more
\item Being Present: less obligations, more natural, more productivity, better quality of work.
\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{How to get rich}

\begin{itemize}
\item There is no skill like Business.
\item Business cannot be learnt in school
\item What you really want is to figure out what Society wants and does not know how to get it yet. You need to provide that and that too, at scale.
\item Mostly dynamic, but if you have specific knowledge that you are passionate about, you can find matching desire from society. Or time brings it to your plate.
\item Need: Specific Knowledge, Accountability to own brand, Leverage/amplification
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Meaning of Life}

\begin{itemize}
\item Nonsense question.
\item One end goal leads to another and so on.
\item These are games, first marks, then education, then job, status, money, etc. Just games.
\item Living the life as it goes.
\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Wealth vs Status}

\begin{itemize}
\item All of us want to be Free.
\item Easiest way to solve money problem by money. Be rich first.
\item Wealth positive sum game. Create more wealth without taking away from anyone.
\item Status is zero sum game. Only one can be number one at the cost of others.
\item Status guys attack Wealth as they cannot get it.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{What to look for in people}

\begin{itemize}
\item In Business: Intelligence, Energy, Integrity
\item In Relationships: Honesty, Calm (emotional self control)
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Philosophy book recommendation}

\begin{itemize}
\item For starters: Siddhartha, Herman Hess
\item For Advanced: Krishnamurthy Total Freedom, Osho Great Challenge, Marcus Meditations
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Modern Struggle}

\begin{itemize}
\item All our diseases are diseases of abundance in the modern times.
\item In old times, of scarcity, you consume whatever you get your hands laid on eg Sugar, News, etc for my survival
\item We are over exposed to everything. Brain can not cope up with that deluge. If you pay attention to all, it will drive you insane. 
\item Social media is addictive like Sugar.
\item Resist. 
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Stress}

	\begin{itemize}
	\item Stress happens when something wants to be in two places at one time. Like iron rod getting pulled from two ends.
	\item Stress is an inability to decide what’s important
	\item You want to find peace from mind. 
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Peace}

	\begin{itemize}
	\item Peace is happiness at rest.
	\item Happiness is Peace in motion.
	\item The ultimate goal is not happiness, even though we use that term a lot. The goal is peace.
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{How do you get to peace?}

	\begin{itemize}
	\item Fundamentally, peace is inactivity; it’s a sense that everything is fine.
	\item If everything is fine, you’re not doing any physical or mental activity to change it. 
	\item You’re also not wishing you were doing something to change it, because that creates stress. 
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{How do you get to peace?}

	\begin{itemize}
	\item You cannot work toward peace, only understanding
	\item ``The name of God is truth.''
	\item If/once you understand true nature of everything, then you are at Peace.
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Meditation}

	\begin{itemize}

	\item Free mind associates with things it sees, then imagines
	\item Contemplating on a subject, various aspects related to them
	\item Concentration is focusing on a topic
	\item Most meditation techniques are of concentration with a hope that at one stage you will be free from the concentration subject. 
	\item Meditation is actually beyond concentration. 
	\item You cannot do meditation. It happens when you are not doing anything. 
	\item Be still 1 hr a day. On one day you will reach a state where no thoughts bubble up.
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Life Formulas}

	\begin{itemize}

	\item Happiness = Health + Wealth + Good Relationships 
\item Health = Exercise + Diet + Sleep 
\item Exercise = High Intensity Resistance Training + Sports + Rest 
\item Diet = Natural Foods + Intermittent Fasting + Plants 
\item Sleep = No alarms + 8–9 hours + Circadian rhythms 
\item Wealth = Income + Wealth * (Return on Investment) 
\item Income = Accountability + Leverage + Specific Knowledge 
\item Accountability = Personal Branding + Personal Platform + Taking Risk? 
\item Leverage = Capital + People + Intellectual Property 
\item Specific Knowledge = Knowing how to do something society cannot yet easily train other people to do 
\item Return on Investment = ``Buy-and-Hold'' + Valuation + Margin of Safety
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Life Rules}

	\begin{itemize}
\item Be present above all else. 
\item Desire is suffering. (Buddha) 
\item Anger is a hot coal you hold in your hand while waiting to throw it at someone else. (Buddha) 
\item If you can't see yourself working with someone for life, don't work with them for a day. 
\item Reading (learning) is the ultimate meta-skill and can be traded for anything else. 
\item All the real benefits in life come from compound interest. 
\item Earn with your mind, not your time. 
\item 99 percent of all effort is wasted. 
\item Total honesty at all times. It's almost always possible to be honest and positive. 
\item Praise specifically, criticize generally. (Warren Buffett) 
\item Truth is that which has predictive power. 
\item Watch every thought. (Ask ``Why am I having this thought?'') 
\item All greatness comes from suffering. 
\item Love is given, not received. 
\item Enlightenment is the space between your thoughts. (Eckhart Tolle) 
\item Mathematics is the language of nature. 
\item Every moment has to be complete in and of itself.
	\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Life Playbook}

Happiness = Health + Wealth + Good relationships
\begin{itemize}
\item Health = Exercise + Diet + Sleep
		\begin{itemize}
		\item Exercise = High Intensity Resistance training + Sports + Rest
		\item Diet = Natural Foods + Intermittent Fasting + Plants
		\item Sleep = No Alarms + 8-9 hours + Circadian Rhythms
		\end{itemize}

\item Wealth = Income + RoI
		\begin{itemize}
		\item Income = Accountability + Leverage + Specific Knowledge
			\begin{itemize}
			\item Accountability = Personal Branding + Personal Platform + Taking Risk
			\item Leverage = Capital + People + Intellectual Property
			\item Specific Knowledge =  Knowing how to do something that society cannot yet easily train other people to do
			\end{itemize}
		\item RoI = Buy-and-Hold + Valuation + Margin of Safety
		\end{itemize}
\end{itemize}


\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Life Play-book Summary}

\begin{itemize}
\item Fast, lift, sprint, stretch, and meditate.
\item Build, sell, write, create, invest, and own.
\item Read, reflect, love, seek truth, and ignore society.
\item Make these habits. Say no to everything else.
\item Avoid debt, jail, addiction, disgrace, shortcuts, and media.
\item Relax. Victory is assured.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large 10 Life-Changing Lessons I Learned From Naval
Ravikant}

{\small - Sergey Faldin}

\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{1. Reading will change your life}

\begin{itemize}
\item ``I always spent money on books''
\item ``I never viewed that as an expense''. 
\item ``That’s an investment to me''
\item  Permit yourself to quit once it becomes boring. No Sunk (lost) cost (time) logic. You have spent so much time on it, so , its a must to finish it. No!!
\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{2. Think long-term}

\begin{itemize}
\item  Realize that things will take time. Success will take time. Fixing
something will take time.
\item ``The best things in life, come as compound interest''
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{3. Self-esteem is the relationship you have with yourself}

\begin{itemize}
\item Self-esteem is, essentially, self-respect
\item  The more you do good things — the more you respect yourself and love yourself. 
\item Every time
you lie, you lie to yourself. And you gradually start to love yourself less and have low self-
esteem.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{4. Use leverage to build a fortune}
In order to get rich, you need:
\begin{itemize}
\item Specific knowledge
\item Accountability (brand)
\item Leverage (amplification)
\begin{itemize}
\item Labor: Delegation, paying to get folks to do tasks
\item Capital: money brings monery
\item  Code and Media: easy replication (near zero marginal cost)
\end{itemize}
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{5. Become the best at what you do}

\begin{itemize}
\item  You can be the best at something small, niche — in
fact, that’s the easiest way to do so.
\item Some people are making the world a better place by just being who they are.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{6. Happiness is a habit}

\begin{itemize}
\item  The reality is life is a single-player game. You’re born alone. You’re going to die alone. All of
your interpretations are alone. All your memories are alone. You’re gone in three
generations and nobody cares. Before you showed up, nobody cared. It’s all single-player.
\item Happiness is something everybody
can train themselves for.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{7. If you want to think differently, you’ve got to read differently}

\begin{itemize}
\item  If you’re searching for success (non-average outcome), you can’t expect
to get that if you make average decisions.
\item  Almost everything that people read these days is designed for social approval
\item Forging your own path will take strength and courage.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{8. Start out by thinking of yourself as a loser}

\begin{itemize}
\item   Then you will do your own thing and you’re much more likely to find that
winning path.
\item  Learn to be just happy being you — with your
weird tastes, desires, and inclinations.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{9. Great people have great outcomes}

\begin{itemize}
\item   You just have to be patient.
\item  While if you wait, allow yourself to get smarter, explore the world, and make
connections, you’ll actually increase your odds of success.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{10. Desire is suffering}

Desire is a contract you make with yourself to be unhappy until you
get what you want.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Top 10 Life Learnings \ldots }

\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{1}
\begin{center}
When looking for a purpose to life, notice that most things are stepping stones, done for ulterior motives.
\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{2}
\begin{center}
If you ever want to have peace in your life, you have to move beyond good and evil.
\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{3}
\begin{center}
 To measure the quality of your life, simply do nothing, and see how it feels.
\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{4}
\begin{center}
No one can compete with you on being you. Most of life is a search for who and what needs you the most.
\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{5}
\begin{center}
Living a life of integrity pays off, but it takes a very long time.
\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{6}
\begin{center}
Three things in life: your health, your mission, and the people you love. That's it.\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{7}
\begin{center}
Play iterated games. All the returns in life, whether in wealth, relationships, or knowledge, come from compound interest.
\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{8}
\begin{center}
Religion, science, and spirituality help us make sense of the world. Life without at least one of them is a lonely and confusing place.
\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{9}
\begin{center}
Life is a single-player game.
\end{center}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{10}
\begin{center}
You can get almost anything you want out of life, as long as it's one thing and you want it far more than anything else.
\end{center}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Bonus}
\begin{center}
Of all the cards you can pick in the game of life, choose intelligence and drive. You can trade those two for almost anything else.
\end{center}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Top 10 Meditation Learnings \ldots }

\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{1}
\begin{center}
Meditation is not you going through thoughts - it’s letting thoughts go through you.
\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{2}
\begin{center}
Yoga cultivates Peace of Body. Meditation cultivates Peace of Mind.
\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{3}
\begin{center}
Meditation and transcendence are the birthrights of every human being..
\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{4}
\begin{center}
Consider meditation as “self-therapy.” Instead of paying a therapist to listen to you, listen to yourself (non-judgmentally) until you accept or drop the fears.
\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{5}
\begin{center}
Meditation, arts and artisan-ship, craftsmanship, politics, are other activities with learning curves detached from physical ability.
\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{6}
\begin{center}
Meditation is turning off society and listening to yourself. It only “works” when done for its own sake.\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{7}
\begin{center}
Insight meditation lets you run your brain in debug mode until you realize that you're just a subroutine in a larger program.
\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{8}
\begin{center}
Perhaps one reason why yoga and meditation are hard to sustain is that they have no extrinsic value. Purely single-player games.
\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{9}
\begin{center}
Meditation is intermittent fasting for the mind. Too much sugar leads to a heavy body, and too many distractions lead to a heavy mind.
\end{center}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{10}
\begin{center}
If meditation was easy, you’d do nothing else.
\end{center}
\end{frame}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Farnam Street talk \ldots }

\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Farnam Street talk}

\begin{itemize}
\item My number one priority in life, above my happiness, above my family, above my work, is my own health.
\item I try and set up good systems and then the individual decisions don’t matter that matter much
\item Science is, to me, the study of truth. It is the only true discipline because it makes falsifiable predictions.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Farnam Street talk}

\begin{itemize}
\item To me, happiness is not about positive thoughts. It’s not about negative thoughts. It’s about the absence of desire, especially the absence of desire for external things.
\item Happiness to me is mainly not suffering, not desiring, not thinking too much about the future or the past, really embracing the present moment and
the reality of what is, the way it is.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Farnam Street talk}

\begin{itemize}
\item I don’t believe that I have the ability to say what is going to work. 
\item Rather, what I try to do is try to eliminate what’s not going to work. 
\item It’s not about having correct judgment. 
\item It’s about avoiding incorrect judgments.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Farnam Street talk}

\begin{itemize}
\item I think all the benefits in life come from compound interest. 
\item I only want to be around people that I know I’m going to be around with for the rest of my life. 
\item I only want to work on things that I know have a long-term payout.
\item I think if you take a very long-term point of view and if you take the emotion out of it, then I wouldn’t consider those things mistakes anymore.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Farnam Street talk}

\begin{itemize}
\item Macroeconomics is a combination of voodoo complex systems and politics. 
\item You can find macroeconomists that take every side of every argument. 
\item I think that discipline, because it doesn’t make falsifiable predictions, which is the hallmark of science, it’s become corrupted.
\item I gave up macro and I embraced micro. I think it’s all micro. It’s like change yourself, then maybe change your family and your neighbor before you get into abstract concepts about I’m going to change the world.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Farnam Street talk}

\begin{itemize}
\item Someone who makes decisions right 80\% of the time instead of 70\% of the time will be valued and compensated in the market hundreds of times more. 
\item With modern technology and large workforces and capital, our decisions are getting leveraged more and more.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Farnam Street talk}

\begin{itemize}
\item Someone who makes decisions right 80\% of the time instead of 70\% of the time will be valued and compensated in the market hundreds of times more. 
\item With modern technology and large workforces and capital, our decisions are getting leveraged more and more.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Predictions}

\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Dis-intermediation}

\begin{itemize}
\item No/less middle men
\item Democratize information
\item Flat world
\item No brokers, no commissions.
\item Direct producer-consumer marketplace
\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Decentralization}

\begin{itemize}
\item Local decision making, quick/responsive
\item On Edge, processing
\item No, big brother control
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Privacy}

\begin{itemize}
\item Streaming cameras all over
\item Every vehicle with a commercial license plate will eventually be Uber-ized. (2012-12-12)
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Culture}

\begin{itemize}
\item Start seeing transparency in politics.  Tune in to watch the President 24/7. 
\item Crowdfunding plus social media means no more elite candidates.
\item On a long enough timescale, everyone will be working for themselves.
\item Robots and computers will own any clearly bounded job, skill or game.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Technology}

\begin{itemize}
\item Sensors, and robotics making computing geo-ubiquitous.
\item Someday people will say, "Remember passwords?" And roll their eyes. (2015-05-29 06:04:45)
\item The iWatch seems like flawless execution of a flawed concept. (2014-09-13)
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Naval is a honeypot for first principle thinkers}

{\small Thiyagarajan Maruthavan (Rajan)}


\end{center}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Principles, Skills}

\begin{itemize}
\item Decision Making — You make good decision when it becomes an instinct ; when
faced with many pick the difficult one
\item Learning — Teaching forces learning; Mastery must be pursued for its own
\item Negotiation — He who cares less wins
\item Managing Time — Do a 2 factor authentication on time commits
\item Speaking — Speak as you write and vice versa; eliminate inner monologue, hear your
own voice, know your subject stone cold
\item Wisdom — Prune bullshit ; is measured by calm in uncertainty; is discarding vice
return to virtue ; Life is a single player game ; Know when to enter the game and exit
the game
\item Happiness — Is a skill ; Is a desire ; Is a contract with self
\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Wealth creation}

\begin{itemize}
\item Comes with owning a business
\item Earn with mind not time ;
\item Is both luck \& skill, early luck is preferable but gives bad habits ;
\item Be optimistic while being a contrarian ;
\item is like poker game, cards you are dealt and hands you play ;
\item Seek mis-priced optionality ;
\item Is about timing and your own time horizons ;
\item Patience trumps cleverness ;
\item Investing as angel is like winning a six digit lottery but knowing one digit.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Individual vs Tribe}

\begin{itemize}
\item Only the individual transcends. There’s no community that’ll get you there. Everybody’s journey is unique.
\item If you attack someone’s identity, you shut down all conversations with them
\item Logic of violence determines the structure of society
\item Uncertainty, not outcome, is the root of stress
\item The problem with getting good at a game, especially one with big rewards, is that you continue playing it long after you should have outgrown it
\item Life is a single player game
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Money}

\begin{itemize}
\item Earn with your mind, not your time
\item Consensus” is just another way of saying ``average''
\item You get paid for being right first, and to be first, you can’t wait for consensus.
\item Best investing attitude is contrarian, patient, informed optimism.
\item Wealth creation is an evolutionarily recent positive-sum game. Status is an old
zero-sum game. Those attacking wealth creation are often just seeking status
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Happiness}

\begin{itemize}
\item Happiness is a state where nothing is lacking.
\item The path to happiness is truth seeking, and the path to truth is understanding.
\item Understand that happiness is a skill that can be learned.
\item You can slowly and methodically improve your happiness baseline
\item Happiness, love \& passion aren’t things you find, they are choices you make.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Happiness: Get your health in order}
\begin{itemize}
\item If you’re not fit enough to make money, hangout with friends or do the things you love - then you are not going to be happy.
\item Health is the foundation of happiness.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Happiness: Chase financial freedom}
\begin{itemize}
\item You cannot buy happiness, but you can buy your way out of common causes of unhappiness.
\item Renunciation is ineffective in the long run - and happiness without material comfort is playing life on hard mode.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Happiness: Have fewer desires}
\begin{itemize}
\item Desire is a contract you make to remain unhappy untill you get what you want.
\item Human wants are insatiable, yet no external thing will make you happy forever.
\item Contentment brings peace, peace brings happiness.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Happiness: Find peace from mind}
\begin{itemize}
\item Peace is happiness at rest, happiness is peace in motion.
\item Happiness makes you peaceful in passivity, peace makes you happy in activity.
\item It’s not about being jovial all the time -
\item  A happy person is someone who effortlessly interprets events in such a way that they don’t lose their inner peace.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Happiness: Be present}
\begin{itemize}
\item Unhappiness comes from
\begin{itemize}
\item comparing the past to the present
\item regretting and wishing things happened differently
\item imagining unreal scenarios
\end{itemize}
\item The human mind is constantly oscillating between the past and the future
\item This causes mental stress and disturbs your inner peace.
\item So catch your mind whenever it wanders and bring it back to the present as much as you can.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Happiness: Avoid envy}
\begin{itemize}
\item Happiness is an internal game, you play against yourself. 
\item When your feel envious of someone - 
\item don’t just choose one aspect of the lives, be ready to do a 100\% + 24/7 swap with them.
\item Do you still want their lives?
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Happiness: Reduce your sense of self}
\begin{itemize}
\item Self-improvement is a recipe for self-conflict.
\item Don’t take yourself seriously, you are just a monkey with a plan.
\item All your accomplishments and shortcomings will go to dust.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Happiness: Avoid things that make you unstable}

\begin{itemize}
\item Avoid
\begin{itemize}
\item Porn
\item Sugar
\item Coffee
\item  Alcohol
\item Video games 
\end{itemize}
\item These things will make you feel good in the short term but could ruin your happiness long term.
\item All screen activities reduce your happiness.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Happiness: Avoid things that make you unstable}

\begin{itemize}
\item Non-screen activities make you more stable and happier.
\begin{itemize}
\item meditate
\item  walk in nature
\item  exercise regularly
\item  get more sunlight
\item  have conversations in real life
\end{itemize}
\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Happiness: Practice acceptance}

\begin{itemize}
\item Acceptance means to be okay with whatever the outcome is.
\item If you want change - make it happen.
\item If you can’t change - accept it.
\item If you can’t accept - leave it.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Happiness: Tell everyone you are happy}

\begin{itemize}
\item Consistency bias will force you to live up to your claim.
\item Make it your mission to be the happiest person you know.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Happiness}

\begin{itemize}
\item Surround yourself with positive and optimistic people
\item Don’t hangout with people who always engage in conflict.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Happiness: Embrace death}

\begin{itemize}
\item Don’t live in denial of death, you are only here for a short while.
\item Enjoy yourself, do something positive and appreciate every moment.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Random Quotes}

\begin{itemize}
\item You get rewarded for unique knowledge, not for effort. Effort is required to create unique knowledge.
\item If you want to make the wrong decision, ask everyone.
\item A busy calendar and a busy mind will destroy your ability to create
anything great.
\item Happiness is a state where nothing is missing.
\item Guard your time. It’s all you have.
\item You do not want to compete, you want to be a market of one. 
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Random Quotes}

\begin{itemize}
\item That’s the fundamental delusion – that there is something out there
that will make you happy forever. 
\item If you could literally just sit for 30 minutes and be happy, you are
successful. 
\item The modern mind is overstimulated and the modern body is
under stimulated and overfed. Meditation, exercise, and fasting
restore an ancient balance.
\item Become the best in the world at what you do. Keep redefining what
you do until this is true.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Random Quotes}

\begin{itemize}
\item Meditation  is intermittent fasting for the mind. Too much sugar leads
to a heavy body, and too many distractions lead to a heavy mind.
Time spent un-distracted and alone, in self-examination, journaling,
meditation, resolves the unresolved and takes us from mentally fat to fit.

\item A happy, calm, and peaceful person will make better decisions. So if
you want to operate at peak performance, you have to learn how to
tame your mind

\item Mentors won’t make you rich. Doctors won’t make you healthy.
Nutritionists won’t make you slim. Teachers won’t make you smart. Gurus won’t make you calm. Trainers won’t make you  t. Ultimately,
you have to take responsibility. Save yourself.

\item When you’re healthy you have 10000 needs, but when you’re sick you
only have one need.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Random Quotes}

\begin{itemize}
\item Sing the song that only you can sing, write the book that only you can
write, build the product that only you can build… live the life that only
you can live.

\item You can escape competition through authenticity, when you realize
that no one can compete with you on being you. That would have
been useless advice pre-Internet. Post-Internet, you can turn that into
a career.

\item You make your own luck if you stay at it long enough.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Random Quotes}

\begin{itemize}
\item The reality is life is a single-player game. You’re born alone. You’re
going to die alone. All of your interpretations are alone. All your
memories are alone. You’re gone in three generations and nobody
cares. Before you showed up, nobody cared. It’s all single-player.

\item You get paid for being right  first, and to be  first, you can’t wait for
consensus.

\item You’ll do better work if you’re bored rather than busy.

\item The world doesn’t always give what you want, but it often gives you
what you need.

\item Learn to sell. Learn to build. If you can do both, you will be
unstoppable
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Random Quotes}

\begin{itemize}
\item If you can’t see yourself working with someone for life, don’t work
with them for a day.

\item A  t body, a calm mind, a house full of love. These things cannot be
bought — they must be earned.

\item All the real benefits in life come from compound interest.

\item The most important trick to be happy is to realize that happiness is a
skill that you develop and a choice that you make. You choose to be
happy, and then you work at it.

\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Random Quotes}

\begin{itemize}
\item You want to be rich and anonymous, not poor and famous.
\item What you do, who you do with, and how you do it are way more
important than how hard you work.
\item Trade money for time, not time for money. You’re going to run out of
time first.
\item Arm yourself with specific knowledge.

\item I would rather read the best hundred books over and over again until I
absorb them rather than read every single book out there.

\item The  first rule of handling conflict is don’t hang around people who are
constantly engaging in conflict.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Random Quotes}

\begin{itemize}
\item Ruthlessly cut meetings out of your life.
\item Relax you’ll live longer and perform better.
\item Happiness is more about peace than it is about joy.
\item The people who succeed are irrationally passionate about something.
\item To the experts, what looks like hard work from the outside, is play
from the inside.
\item If you want to operate at peak performance, you have to learn how to
tame your mind.
\item Pick your one overwhelming desire. It’s okay to su er over that one.
But on all the other desires, let them go so you can be calm and
peaceful and relaxed.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Random Quotes}

\begin{itemize}
\item You’re better o  following your genuine intellectual curiosity rather
than chasing whatever is hot right now.
\item Today in society you get rewarded for creative work, for creating
something brand new that society didn’t even know that it wanted
that it doesn’t yet know how to get, other than through you.

\item The best way to prepare for the future 20 years is  nd something you
love to do, to have a shot at being one of the best people in the world
at it. Build an independent brand around it, with your name, not a
company’s name or other people’s names around it. Try to make a
creative work, so you’ll stay interesting, stay ahead of the game.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Random Quotes}

\begin{itemize}
\item Figure out what you’re good at and start helping other people with it;
give it away. Pay it forward. Karma sort of works because people are
very consistent. On a long enough timescale, you will attract what
you project.

\item  A contrarian reasons independently, from the ground
up, and resists pressure to conform.
\item Asymmetric opportunities: Invest in startups. Start a company. Create
a book, podcast, video. Create a (software) product. Go on many  rst
dates. Go to a cocktail party. Read a Lindy book. Move to a big city.
Buy Bitcoin. Tweet.

\item Once you’ve truly controlled your own fate, for better or for worse,
you’ll never let anyone else tell you what to do.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Random Quotes}

\begin{itemize}
\item You’re meant to do something. You’re not just meant to lie there in
the sand and meditate all day long. You should self-actualize. You
should do what you are meant to do.

\item ‘Consensus’ is just another way of saying ‘average’.

\item A good conference is a vacation that you take with really smart
friends.

\item If you can’t delete an email without  inching or responding, you won’t
scale.

\item Given that the main function of universities these days is  filtering and
signaling, the best move is to get admitted to Stanford and then drop
out.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Random Quotes}

\begin{itemize}
\item If you’re smart, you should be able to figure out how to be happy.
Otherwise, you’re not that smart.

\item You have social statisticians, scientists, and researchers in lab coats,
literally the best minds of our generation  figuring out how to addict
you to the news. And if you fall for it, if you get addicted. your brain
will get destroyed. 

\item The fundamental insecurity – most people need faith in something –
religion, government, academia. Few are comfortable with
decentralized systems.

\item All greatness comes from suffering.

\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Random Quotes}

\begin{itemize}
\item If you want to see who rules over you, see who you’re not allowed to
criticize.
\item To measure the quality of your life, simply do nothing, and see how it
feels.
\item My de nition of wisdom is knowing the long term consequences of
your actions.

\item The people with the best judgment are among the least emotional.

\item You can neither give happiness, nor receive it.

\item Yoga cultivates Peace of Body. Meditation cultivates Peace of Mind.

\item On meditation: Sit down, close your eyes, get in a comfortable
position, and whatever happens, happens. If you think, you think. If
you don’t think, you don’t think. Don’t put any effort into it.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Random Quotes}

\begin{itemize}
\item Knowing how little you matter is very important for your own mental
health and happiness.

\item Uncertainty, not outcome, is the root of stress.

\item I think to have peace of mind, you have to have peace of body, first.

\item Looking forward to holidays takes the joy out of everyday.

\item Money will solve all your money problems but it doesn’t get you
everywhere.

\item If you can’t code, write books and blogs, record videos and podcasts.

\item Having a million-dollar net worth doesn’t make you a genius, and
having less than a million-dollar net worth doesn’t make you a fool.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Random Quotes}

\begin{itemize}
\item Notifications are just alarm clocks that someone else is setting for
you.
\item Building technology means you don’t have to choose between
practicing science, commerce, and art.
\item In the digital world, the upside is so large that there’s almost no such
thing as risk.
\item If they can train you to do it, then eventually they will train a computer
to do it.
\item  Things like Twitter and Facebook are not making you happy.
They are making you unhappy.

\item The bigger problem this generation will face is adult education, not
child education
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Random Quotes}

\begin{itemize}
\item I no longer track books read or even care about books read. It’s about
understanding concepts

\item I feel no obligation whatsoever to  nish the book. If at some point I
decide the book is boring, or if it’s got pieces of it that are incorrect so
now I can’t trust the rest of the information in there, I just delete it.

\item Sometimes people wrap long books around simple ideas.

\item The best founders I know listen to and read everyone, but then they
ignore everyone and make up their own mind.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Random Quotes}

\begin{itemize}
\item You have just one life.
\item Pick one desire, and one desire only. The universe will help
you get it. Let go of everything else.
\item  TAMING YOUR MIND: Clear Mind $\rightarrow$ Better Judgement $\rightarrow$ Better
Outcome
\item All the returns in life, whether in wealth, relationships, or knowledge, come from compound interest
 
\item Embrace accountability and take business risks under your own name. Society will reward you with responsibility, equity, and leverage
 
\item If you can outsource something or not do something for less than your hourly rate, outsource it or don’t do it
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{ Random Quotes}

\begin{itemize}
\item The less you want something, the less you’re thinking about it, the less you’re obsessing over it, the more you’re going to do it in a natural way
 
\item Forget rich versus poor, white-collar versus blue. It’s now leveraged versus un-leveraged
 
\item Forty hour work weeks are a relic of the Industrial Age. Knowledge workers function like athletes — train and sprint, then rest and reassess
 
\item Earn with your mind, not your time
 
\item I would rather be a failed entrepreneur than someone who never tried. Because even a failed entrepreneur has the skill set to make it on their own
 
\item Most of the gains in life come from suffering in the short term so you can get paid in the long term
 
\item My definition of wisdom is knowing the long-term consequences of your actions. Wisdom applied to external problems is judgment
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Work and Productivity}
      \begin{itemize}
        \item “Forty hour workweeks are a relic of the Industrial Age. Knowledge workers function like athletes — train and sprint, then rest and reassess.”
        \item “People spend too much time doing and not enough time thinking about what they should be doing.”
        \item “The problem happens when we have multiple desires. When we have fuzzy desires. When we want to do ten different things and we’re not clear about which is the one we care about.”
        \item “If you try to micromanage yourself all you’re going to do is make yourself miserable.”
        \item “I don’t plan. I’m not a planner. I prefer to live in the moment and be free and to flow and to be happy.”
        \item “If it entertains you now but will bore you someday, it’s a distraction. Keep looking.”
        \item “I don’t have time is just saying it’s not a priority.”
      \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Wealth and Business}
      \begin{itemize}
        \item “Earn with your mind, not your time.”
        \item “You’re never going to get rich renting out your time.”
        \item “If you see a get rich quick scheme, that’s someone else trying to get rich off of you.”
        \item “Who you do business with is just as important as what you choose to do.”
        \item “If you can’t see yourself working with someone for life, don’t work with them for a day.”
        \item “Above ‘product-market fit’ is ‘founder-product-market fit.’”
        \item “Escape competition through authenticity.”
        \item “Smart money is just dumb money that’s been through a crash.”
      \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Learning and Knowledge}
      \begin{itemize}
        \item “Success is the enemy of learning. It can deprive you of the time and the incentive to start over. Beginner’s mind also needs beginner’s time.”
        \item “Even today, what to study and how to study it are more important than where to study it and for how long.”
        \item “Knowledge is a skyscraper. You can take a shortcut with a fragile foundation of memorization, or build slowly upon a steel frame of understanding.”
        \item “Lots of literacy in modern society, but not enough numeracy.”
        \item “One of the most damaging and widespread social beliefs is the idea that most adults are incapable of learning new skills.”
        \item “Following your genuine intellectual curiosity is a better foundation for a career than following whatever is making money right now.”
        \item “The best teachers are on the Internet. The best books are on the Internet. The best peers are on the Internet.”
      \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Happiness and Peace}
      \begin{itemize}
        \item “Happiness is a choice and a skill and you can dedicate yourself to learning that skill and making that choice.”
        \item “The most important trick to be happy is to realize that happiness is a choice that you make and a skill that you develop.”
        \item “Happiness is a state where nothing is missing.”
        \item “This is such a short and precious life that it’s really important that you don’t spend it being unhappy.”
        \item “Be present above all else.”
        \item “A rational person can find peace by cultivating indifference to things outside of their control.”
        \item “A fit body, a calm mind, a house full of love. These things cannot be bought — they must be earned.”
        \item “Caught in a funk? Use meditation, music, and exercise to reset your mood.”
      \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Habits and Discipline}
      \begin{itemize}
        \item “The power to make and break habits and learning how to do that is really important.”
        \item “Humans are basically habit machines… learning how to break habits is actually a very important meta skill.”
        \item “All the benefits in life come from compound interest — money, relationships, habits — anything of importance.”
        \item “All the real benefits of life come from compound interest.”
        \item “Doctors won’t make you healthy. Nutritionists won’t make you slim. Teachers won’t make you smart. Gurus won’t make you calm. Mentors won’t make you rich. Trainers won’t make you fit. Ultimately, you have to take responsibility. Save yourself.”
      \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Truth and Thinking Clearly}
      \begin{itemize}
        \item “Think clearly from the ground up. Understand and explain from first principles. Ignore society and politics. Acknowledge what you have. Control your emotions.”
        \item “Clear thinkers appeal to their own authority.”
        \item “Truth is that which has predictive power.”
        \item “Watch every thought. Always ask, why am I having this thought?”
        \item “Before you can lie to another, you must first lie to yourself.”
        \item “Total honesty at all times. It’s almost always possible to be honest & positive.”
        \item “To be honest, speak without identity.”
      \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Technology and Progress}
      \begin{itemize}
        \item “Technology is not only the thing that moves the human race forward, but it’s the only thing that ever has.”
        \item “Technology is applied science. Science is the study of nature. Mathematics is the language of nature. Philosophy is the root of mathematics.”
        \item “If they can train you to do it, then eventually they will train a computer to do it.”
        \item “Objectively, the world is improving. To the elites, it’s falling apart as their long-lived institutions are flattened by the Internet.”
        \item “Society has had multiple stores of value... Crypto is the first that’s decentralized *and* digital.”
        \item “Crypto is a bet against the modern macroeconomic dogma, which is passed off as science, but is really a branch of politics.”
      \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Society and Politics}
      \begin{itemize}
        \item “Wealth creation is an evolutionarily recent positive-sum game. Status is an old zero-sum game.”
        \item “Don’t debate people in the media when you can debate them in the marketplace.”
        \item “Politics is sports writ large — pick a side, rally the tribe, exchange stories confirming bias.”
        \item “Politics is the exercise of power without merit.”
        \item “Signaling virtue is a vice.”
        \item “Cynicism is easy. Mimicry is easy. Optimistic contrarians are the rarest breed.”
        \item “Social media has degenerated into a deafening cacophony of groups signaling and repeating their shared myths.”
        \item “School, politics, sports, and games train us to compete against others. True rewards... come from ignoring others and improving ourselves.”
      \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Life, Mortality and Meaning}
      \begin{itemize}
        \item “The fundamental delusion — there is something out there that will make me happy and fulfilled forever.”
        \item “We’re not really here for that long and we don’t really matter that much. And nothing that we do lasts.”
        \item “If you’re desensitized to the fact that you’re going to die, consider it a different way. As far as you’re concerned, this world is going to end. Now what?”
        \item “Desire is a contract that you make with yourself to be unhappy until you get what you want.”
        \item “Every moment has to be complete in and of itself.”
        \item “Reality is neutral. Our reactions reflect back and create our world.”
        \item “You can change it, you can accept it, or you can leave it. What is not a good option is to sit around wishing...”
      \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Ethics and Character}
      \begin{itemize}
        \item “Don’t do things that you know are morally wrong. Not because someone is watching, but because you are.”
        \item “Self-esteem is just the reputation that you have with yourself.”
        \item “If you don’t love yourself who will?”
        \item “Morality and ethics automatically emerge when we realize the long term consequences of our actions.”
        \item “Love is given, not received.”
        \item “Anger is a hot coal that you hold in your hand while waiting to throw it at someone else.” (Buddhist saying)
        \item “All greatness comes from suffering.”
      \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Time and Attention}
      \begin{itemize}
        \item “A busy mind accelerates the perceived passage of time. Buy more time by cultivating peace of mind.”
        \item “You can have the mind or you can have the moment.”
        \item “So I have no time for short-term things: dinners with people I won’t see again, tedious ceremonies to please tedious people...”
        \item “A personal metric: how much of the day is spent doing things out of obligation rather than out of interest?”
        \item “You have to surrender, at least a little bit, to be the best version of yourself possible.”
      \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Life, Happiness \& Peace of Mind}
\begin{itemize}
  \item A fit body, a calm mind, a house full of love. These things cannot be bought, they must be earned. तंदुरुस्त शरीर, शांत मन आणि प्रेमाने भरलेले घर – हे विकत घेता येत नाहीत, कमवावे लागतात.

  \item This is such a short and precious life that it’s really important that you don’t spend it being unhappy. आपलं आयुष्य इतकं छोटे आणि मौल्यवान आहे, ते दु:खी होण्यात वाया घालवू नका.

  \item Happiness is a choice and a skill and you can dedicate yourself to learning that skill and making that choice. आनंदी असणं स्वतःची इच्छा आणि कौशल्य आहे. आपलं आयुष्य हे त्या इच्छेसाठी आणि कौशल्य विकसित करण्यासाठी खर्ची घाला.

  \item The most important trick to be happy is to realize that happiness is a choice that you make and a skill that you develop. आनंदी होण्याचा सर्वात मोठा मंत्र म्हणजे आनंद ही तुमची निवड आहे हे ओळखणे आणि त्या निवडीचं कौशल्य जपण्यात आहे. 

  \item Happiness is a state where nothing is missing. आनंद म्हणजे अशी अवस्था आहे जिथे कमतरतेचा मागमूसही नसतो. 

  \item Reality is neutral. Our reactions reflect back and create our world. वास्तव हे निर्विकार आहे. आपली प्रतिक्रिया या वास्तवात आपलं जग निर्माण करते. 

  \item A rational person can find peace by cultivating indifference to things outside of their control. तर्कशुद्ध व्यक्ती त्याच्या नियंत्रणाबाहेरील गोष्टींबद्दल उदासीन राहून (दुर्लक्ष करून) शांतता मिळवते. 

  \item The enemy of peace of mind is expectations drilled into you by society and other people. मन:शांतीचा शत्रू म्हणजे समाज आणि लोकांनी रुजवलेल्या अपेक्षा होत. 

  \item Anger is a hot coal that you hold in your hand while waiting to throw it at someone else. राग म्हणजे दुसऱ्यावर फेकायचे जळते निखारे स्वतःच्या हातात ठेवणे.

  \item Caught in a funk? Use meditation, music, and exercise to reset your mood. अस्वस्थ वाटतंय? तर मनःस्थिती बदलण्यासाठी ध्यान, संगीत किंवा व्यायाम याचा वापर करा

  \item Be present above all else. सर्वप्रथम वर्तमानात रहा. 

  \item Every moment has to be complete in and of itself. प्रत्येक क्षण वर्तमानात राहून अनुभवावा. 

  \item You can have the mind or you can have the moment. एकतर तुम्ही हा क्षण कसा जगायचा हा विचार करत बसू शकता किंवा तो क्षण जगू शकता. दोन्ही एकत्र नाही होऊ शकत. 

  \item A busy mind accelerates the perceived passage of time. Buy more time by cultivating peace of mind. व्यस्त असलेल्या मनाला काळ वेळाचं भान राहत नाही. जास्त वेळ मिळावा असं वाटत असेल तर मन:शांती चा मार्ग धरा.  

  \item Life hack: when in bed, meditate. Either you will have a deep meditation or fall asleep. Victory either way. जीवनमंत्र: झोपताना ध्यान करा. एक तर ध्यान चांगलं लागेल किंवा छान झोप लागेल, दोन्ही फायदेशीर. 

  \item Meditation is intermittent fasting for the mind. ध्यान म्हणजे मनासाठीचा उपवास. 

  \item Enlightenment is the space between your thoughts. ज्ञान म्हणजे तुमच्या विचारांमधील रिक्त जागा.

  \item You can change it, you can accept it, or you can leave it. What is not a good option is to sit around wishing. एक तर तुम्ही बदलू शकता, स्वीकारू शकता किंवा सोडू शकता – पण फक्त इच्छा करत बसणे निरर्थक आहे. 
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Wealth, Work \& Entrepreneurship}
\begin{itemize}
  \item Earn with your mind, not your time. तुमच्या वेळेने नव्हे तर बुद्धीने कमवा.

  \item You’re never going to get rich renting out your time. वेळ भाड्याने देऊन कोणी श्रीमंत होत नाही.

  \item Wealth is assets that earn while you sleep. धन म्हणजे तुम्ही झोपलेले असतानाही कमावणारी साधने.

  \item You must own equity to gain your financial freedom. आर्थिक स्वातंत्र्यासाठी मालकी हक्क (इक्विटी) असणे आवश्यक आहे.

  \item Apply specific knowledge with leverage and eventually, you will get what you deserve. विशेष ज्ञान आणि साधनांचा उपयोग करा – शेवटी योग्य फळ मिळेल.

  \item Play long-term games with long-term people. दीर्घकालीन खेळायचं असेल तर दूरदृष्टीच्या लोकांसोबत राहा/खेळा .

  \item Embrace accountability and take business risks under your own name. Society will reward you with responsibility, equity, and leverage. जबाबदारी स्वीकारा आणि स्वतःच्या नावाने धोका स्वीकारा, समाज तुम्हाला मालकी आणि लाभ देईल.

  \item Forget rich versus poor, white-collar versus blue. It’s now leveraged versus un-leveraged. 
गरीब की श्रीमंत, पांढरपेशी कि रोजंदारीवाले या फरकांवर आजकाल काही अवलंबून नाहीये. आत्ताची स्पर्धा  ज्यांच्याकडे साधने आहेत आणि ज्यांच्याकडे नाहीत यांच्यात आहे.

  \item Who you do business with is just as important as what you choose to do. तुम्ही कोणाबरोबर व्यवसाय करता हे, तुम्ही काय करता याइतकेच महत्त्वाचे आहे.

  \item If you can’t see yourself working with someone for life, don’t work with them for a day. ज्यांच्याशी आयुष्यभर काम करू शकत नाही असं वाटतं, त्यांच्याबरोबर एक दिवसही काम करू नका.

  \item Don’t partner with cynics and pessimists; their beliefs are self-fulfilling. निंदक आणि निराशावादी लोकांशी भागीदारी करू नका, त्यांची श्रद्धा स्वतः पुरतीच असते.

  \item Escape competition through authenticity. प्रामाणिकपणातून स्पर्धा टाळा.

  \item Above ``product-market fit'' is ``founder-product-market fit.'' ``उत्पादन-बाजार जुळणी'' पेक्षा महत्त्वाची म्हणजे ``संस्थापक-उत्पादन-बाजार जुळणी.''

  \item I would rather be a failed entrepreneur than someone who never tried. प्रयत्न न करणाऱ्या व्यक्तीपेक्षा अपयशी उद्योजक असणे पसंत करीन.

  \item Grind and sweat, toil and bleed, face the abyss. It’s all part of becoming an overnight success. कष्ट, संघर्ष आणि वेदना – हे सर्व एका क्षणात मिळालेल्या यशाचा भाग आहेत.

  \item If you see a get rich quick scheme, that’s someone else trying to get rich off of you. जलद श्रीमंतीच्या योजनेत तुमचा वापर करून दुसरा श्रीमंत होतो.

  \item Retirement is when you stop sacrificing today for an imaginary tomorrow. निवृत्ती म्हणजे काल्पनिक उद्यासाठी आजचा त्याग थांबवणे.

  \item Forty hour workweeks are a relic of the Industrial Age. Knowledge workers function like athletes, train and sprint, then rest and reassess. ४० तासांचा आठवडा ही औद्योगिक काळाची परंपरा आहे. ज्ञानकर्मी खेळाडूसारखे – प्रशिक्षण मग जलदगतीने धावणे, आणि मग विश्रांती घेत मागोवा घेणे. 
\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Work, Wealth \& Success}
\begin{itemize}
    \item ``Most of the gains in life come from suffering in the short term so you can get paid in the long term.'' आयुष्यातील बहुतांश फायदा हा अल्प-काळात सोसलेल्या त्रासातून येतो, जेणेकरून दीर्घकाळात त्याचे फळ मिळते.

    \item ``All the returns in life, whether in wealth, relationships, or knowledge, come from compound interest.'' 
आयुष्यातील सर्व परतावे, संपत्ती, नातेसंबंध किंवा ज्ञान, हे चक्रवाढ व्याजातून येतात.
\end{itemize}

\section*{Learning \& Knowledge}
\begin{itemize}
    \item ``The most important skill for getting rich is becoming a perpetual learner.'' श्रीमंत होण्यासाठीची सर्वात महत्त्वाची कौशल्य म्हणजे कायम शिकत राहणे.

    \item ``Your most important skill isn’t even what you majored in... it’s just knowing how to learn.'' तुमचे सर्वात महत्त्वाचे कौशल्य म्हणजे तुम्ही काय शिकलात हे नाही, तर कसे शिकायचे हे आहे.

    \item ``Even today, what to study and how to study it are more important than where to study it...'' आजही काय शिकायचे आणि कसे शिकायचे हे कुठे शिकायचे यापेक्षा महत्त्वाचे आहे.

    \item ``Read what you love until you love to read.'' जोपर्यंत वाचनाची आवड निर्माण होत नाही तुम्हाला जे वाचायला आवडते ते वाचा. .

    \item ``It’s better to read a great book slowly than to fly through a hundred books quickly.'' शंभर पुस्तके झपाट्याने वाचण्यापेक्षा एक चांगलं पुस्तक हळूहळू वाचणे चांगले.

    \item ``Knowledge is a skyscraper. You can take a shortcut... or build slowly upon a steel frame of understanding.'' ज्ञान म्हणजे गगनचुंबी इमारत आहे. ती तुम्ही शॉर्टकटने नाजूक पायावर बांधू शकता किंवा हळूहळू समजुतीच्या मजबूत चौकटीवर बांधू शकता.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Work, Wealth \& Success}
\begin{itemize}
    \item ``Most of the gains in life come from suffering in the short term so you can get paid in the long term.'' आयुष्यातील बहुतांश फायदा हा अल्प-काळात सोसलेल्या त्रासातून येतो, जेणेकरून दीर्घकाळात त्याचे फळ मिळते.

    \item ``All the returns in life, whether in wealth, relationships, or knowledge, come from compound interest.'' 
आयुष्यातील सर्व परतावे, संपत्ती, नातेसंबंध किंवा ज्ञान, हे चक्रवाढ व्याजातून येतात.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Learning \& Knowledge}
\begin{itemize}
    \item ``The most important skill for getting rich is becoming a perpetual learner.'' श्रीमंत होण्यासाठीची सर्वात महत्त्वाची कौशल्य म्हणजे कायम शिकत राहणे.

    \item ``Your most important skill isn’t even what you majored in... it’s just knowing how to learn.'' तुमचे सर्वात महत्त्वाचे कौशल्य म्हणजे तुम्ही काय शिकलात हे नाही, तर कसे शिकायचे हे आहे.

    \item ``Even today, what to study and how to study it are more important than where to study it...'' आजही काय शिकायचे आणि कसे शिकायचे हे कुठे शिकायचे यापेक्षा महत्त्वाचे आहे.

    \item ``Read what you love until you love to read.'' जोपर्यंत वाचनाची आवड निर्माण होत नाही तुम्हाला जे वाचायला आवडते ते वाचा. .

    \item ``It’s better to read a great book slowly than to fly through a hundred books quickly.'' शंभर पुस्तके झपाट्याने वाचण्यापेक्षा एक चांगलं पुस्तक हळूहळू वाचणे चांगले.

    \item ``Knowledge is a skyscraper. You can take a shortcut... or build slowly upon a steel frame of understanding.'' ज्ञान म्हणजे गगनचुंबी इमारत आहे. ती तुम्ही शॉर्टकटने नाजूक पायावर बांधू शकता किंवा हळूहळू समजुतीच्या मजबूत चौकटीवर बांधू शकता.
\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Habits \& Self-Mastery}
\begin{itemize}
    \item ``Humans are basically habit machines… learning how to break habits is a very important meta skill.'' माणसे म्हणजे सवयीचे गुलाम आहेत... सवयी बदलण्याचे कौशल्य खूप महत्त्वाचे आहे.

    \item ``The power to make and break habits and learning how to do that is really important.'' सवयी लावणे आणि मोडणे तसेच ते कसे करायचे हे शिकणे फार महत्त्वाचे आहे.

    \item ``The enemy of peace of mind is expectations drilled into you by society and other people.'' मनःशांतीचा शत्रू म्हणजे समाज आणि इतरांनी तुमच्यात रुजवलेल्या अपेक्षा.

    \item ``A busy mind accelerates the perceived passage of time. Buy more time by cultivating peace of mind.'' व्यस्त असलेल्या मनाला काळ वेळाचं भान राहत नाही. जास्त वेळ मिळावा असं वाटत असेल तर मन:शांती चा मार्ग धरा.
\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Philosophy \& Clarity}
\begin{itemize}
    \item ``Happiness is a choice and a skill and you can dedicate yourself to learning that skill and making that choice.'' आनंदी असणं स्वतःची इच्छा आणि कौशल्य आहे. आपलं आयुष्य हे त्या इच्छेसाठी आणि कौशल्य विकसित करण्यासाठी खर्ची घाला.

    \item ``Desire is a contract that you make with yourself to be unhappy until you get what you want.'' इच्छा/वासना/अपेक्षा - स्वतःसोबत केलेला असा करार आहे की जो पूर्ण होईपर्यंत तुम्ही दुःखी राहाल.

    \item ``Be present above all else.'' सर्वात महत्त्वाचे म्हणजे वर्तमानात रहा.

    \item ``Reality is neutral. Our reactions reflect back and create our world.''वास्तव हे निर्विकार आहे. आपली प्रतिक्रिया या वास्तवात आपलं जग निर्माण करते.

    \item ``A rational person can find peace by cultivating indifference to things outside of their control.'' तर्कशुद्ध व्यक्ती त्याच्या नियंत्रणाबाहेरील गोष्टींबद्दल उदासीन राहून (दुर्लक्ष करून) शांतता मिळवते.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Society \& Politics}
\begin{itemize}
    \item ``Wealth creation is an evolutionarily recent positive-sum game. Status is an old zero-sum game.'' संपत्ती निर्माण करणे ही अलीकडची सर्वहिताचा खेळ आहे. प्रतिष्ठा ही जुनी एकाचा नफा तर दुसऱ्याचा तोटा असा खेळ आहे.

    \item ``Politics is sports writ large, pick a side, rally the tribe, exchange stories confirming bias, hurl insults.'' राजकारण म्हणजे मोठ्या प्रमाणावरचा खेळ आहे, बाजू निवडा, गट जमवा, पूर्वग्रह दृढ करणाऱ्या कथा सांगा, शिवीगाळ करा.

    \item ``Don’t debate people in the media when you can debate them in the marketplace.'' माध्यमांवर लोकांशी वाद का घालायचा जर त्यांना आपण बाजारपेठेत आणून वाद घालू शकतो.

    \item ``Signaling virtue is a vice.'' गुण दाखवण्याचा प्रयत्न करणे हा एक दुर्गुण आहे.
\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Technology \& Progress}
\begin{itemize}
    \item ``Technology is not only the thing that moves the human race forward, but it’s the only thing that ever has.'' मानवजातीला पुढे नेणारी एक आणि एकमेव गोष्ट म्हणजे तंत्रज्ञान.

    \item ``The democratization of technology allows anyone to be a creator, entrepreneur, scientist. The future is brighter.'' तंत्रज्ञानाचे लोकशाहीकरण कोणालाही निर्माता, उद्योजक, शास्त्रज्ञ बनण्याची संधी देते. भविष्य उज्ज्वल आहे.

    \item ``The Internet allows you to scale any niche obsession.'' इंटरनेट तुम्हाला कोणत्याही खास आवडीला मोठे करण्याची संधी देते.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Miscellaneous Wisdom}
\begin{itemize}
    \item ``Don’t take yourself so seriously. You’re just a monkey with a plan.'' स्वतःला इतके गंभीरतेने घेऊ नका. तुम्ही फक्त एका योजना असलेलं माकड आहात.

    \item ``Love is given, not received.'' प्रेम हे दिले जाते, मिळवले जात नाही.

    \item ``Anger is a hot coal that you hold in your hand while waiting to throw it at someone else.'' राग म्हणजे दुसऱ्यावर फेकायचे जळते निखारे स्वतःच्या हातात ठेवणे.

    \item ``My 1 repeated learning in life: ‘There Are No Adults.’ Everyone’s making it up as they go along.'' माझ्या आयुष्यातला एक धडा: ‘इथे कोणीही प्रौढ नाही.’ सगळे आपापल्या पद्धतीने शिकत चालले आहेत.
\end{itemize}
\end{frame}

