%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Notes of Talks of Daniel Schmachtenberger!!}

\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Daniel Schmachtenberger's talk at Emergence}

\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Understanding Emergence and Synergy}
	\begin{itemize}
	\item Emergence: New properties arise that weren't present before (e.g., living cell from non-living molecules)
	\item Synergy: Whole systems exhibit properties not found in parts taken separately
	\item Emergent properties are fundamentally unpredictable from individual components
	\item Requires elegant ordered complexity, not just random combinations
	\item More meaningful synergies emerge from combining different elements rather than similar ones
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Attractive Forces and Evolution}
	\begin{itemize}
	\item All emergence stems from physical forces (gravity, electromagnetism) and metaphysical forces (love, shared purpose)
	\item Evolution selects for systems with most advantageous emergent properties
	\item Universe moves toward more elegant ordered complexity through self-organization
	\item Drives both increasing diversity and sophisticated unification
	\item Evolution progresses through relationship, synergy, and emergence
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Consciousness and Human Role}
	\begin{itemize}
	\item Consciousness evolves: reptilian (pain/pleasure) → mammalian → neocortical → prefrontal (abstraction)
	\item Humans can understand deep past and future through abstract thinking
	\item Each individual represents unique facet of universal evolution
	\item Competition becomes obsolete as evolution favors differentiation and symbiosis
	\item Humans can consciously participate in and direct evolution
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Current Systems and Future Directions}
	\begin{itemize}
	\item Global systems show simultaneous exponential improvements and degradation
	\item Modern challenges require coordinated global solutions
	\item Future requires alignment of individual incentives with collective well-being
	\item Infrastructure must shift from linear to closed-loop materials economy
	\item Success of individual inseparable from success of whole system
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Emergence in Practice}
	\begin{itemize}
	\item Bringing components together requires specific patterns of order
	\item Not every relationship is synergistic - some are entropic
	\item System destabilization indicates potential phase shift
	\item Need to move from differential advantage to systemic advantage
	\item Local problems have become extinct in our interconnected world
	\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Daniel Schmachtenberger's findings from ChatGPT in Systems Thinkning}

\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Multi-Scale Feedback Integration}
	\begin{itemize}
	\item Systems function best when \textbf{feedback loops} operate at \textbf{multiple scales} (individual, organizational, societal).
	\item Modern governance and economic systems fail due to \textbf{deferred or broken feedback loops}, leading to externalities like pollution and inequality.
	\item \textbf{Solution:} Internalize externalities by designing \textbf{incentive systems} that correct distortions in real-time.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Avoiding Perverse Incentives in System Design}
	\begin{itemize}
	\item Many systems create \textbf{self-terminating dynamics} by rewarding short-term benefits at long-term costs.
	\item Example: Profit-driven healthcare optimizes for \textbf{treatment, not health}; social media optimizes for \textbf{engagement, not truth}.
	\item \textbf{Solution:} Design \textbf{anti-fragile incentive structures} that align individual and collective interests.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Omni-Win Solutions for Complex Problems}
	\begin{itemize}
	\item Complex problems require \textbf{win-win solutions} rather than zero-sum approaches.
	\item Many interventions solve one problem while \textbf{creating new problems} (e.g., green energy solutions that require rare-earth mining).
	\item \textbf{Solution:} Apply \textbf{higher-order thinking} to ensure interventions don’t generate \textbf{hidden failure modes}.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Game Theory and Transcending Rivalrous Dynamics}
	\begin{itemize}
	\item Most human systems are based on \textbf{zero-sum, win-lose competition} (politics, economy, geopolitics).
	\item If unchecked, \textbf{rivalrous dynamics} escalate toward \textbf{self-destruction} (Mutually Assured Destruction - MAD).
	\item \textbf{Solution:} Shift from \textbf{win-lose to win-win} games through \textbf{cooperative frameworks and decentralized governance}.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Civilization as a Complex Adaptive System (CAS)}
	\begin{itemize}
	\item Human civilization is \textbf{not a linear machine but a complex, adaptive system}.
	\item Small perturbations can lead to \textbf{disproportionate, cascading effects} (butterfly effect).
	\item \textbf{Solution:} Adopt \textbf{adaptive governance} models that evolve in real time, rather than rigid bureaucratic structures.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Existential Risks and Proactive Systems Thinking}
	\begin{itemize}
	\item Technological growth is \textbf{outpacing governance and ethics} (AI, synthetic bio, geoengineering).
	\item Most governance models are \textbf{reactive}, meaning we don’t regulate risks until after damage is done.
	\item \textbf{Solution:} Shift toward \textbf{proactive, anticipatory governance models} that assess risks \textbf{before} they become catastrophic.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{The Importance of Systems Literacy}
	\begin{itemize}
	\item Most societal failures stem from \textbf{poor systems literacy}.
	\item People tend to apply \textbf{linear cause-effect reasoning} to \textbf{nonlinear, complex problems}.
	\item \textbf{Solution:} Teach \textbf{systems thinking, cybernetics, and complexity science} as \textbf{core educational pillars}.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{The Information Ecology Problem}
	\begin{itemize}
	\item \textbf{Epistemic failure} (bad information, polarization, propaganda) is a root failure mode of civilization.
	\item Many societal breakdowns come from \textbf{broken information ecosystems} (misaligned media incentives, lack of critical thinking).
	\item \textbf{Solution:} Develop \textbf{trustworthy sense-making systems} that optimize for \textbf{truth, not engagement}.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Transcending Nation-State Models}
	\begin{itemize}
	\item The \textbf{nation-state model} is inherently adversarial (nationalism breeds competition).
	\item Global challenges (climate change, pandemics, AI risks) require \textbf{global cooperation}.
	\item \textbf{Solution:} Explore \textbf{decentralized, polycentric governance} models that allow for \textbf{local agency but global coordination}.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{The Importance of Regenerative Systems}
	\begin{itemize}
	\item Most economic and industrial models are \textbf{extractive}, not \textbf{regenerative}.
	\item A viable future requires \textbf{regenerative economics, regenerative agriculture, and circular design principles}.
	\item \textbf{Solution:} Transition from \textbf{degenerative industrialization} to \textbf{regenerative planetary stewardship}.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Daniel Schmachtenberger's findings from ChatGPT in Neuro Hacking and self improvements}

\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Neuroplasticity and Cognitive Enhancement}
	\begin{itemize}
	\item The brain is highly adaptable and can rewire itself through \textbf{neuroplasticity}.
	\item Habits, learning, and skill acquisition are optimized by \textbf{targeted, consistent practice}.
	\item \textbf{Solution:} Engage in \textbf{deliberate practice, spaced repetition, and mindfulness techniques} to enhance cognitive function.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Optimizing Neurochemistry for Performance}
	\begin{itemize}
	\item Neurotransmitters like \textbf{dopamine, serotonin, and acetylcholine} govern focus, mood, and learning.
	\item Poor lifestyle choices lead to \textbf{neurochemical imbalances}, affecting motivation and mental clarity.
	\item \textbf{Solution:} Optimize neurochemistry through \textbf{proper nutrition, exercise, sleep, and nootropic support}.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Sleep and Cognitive Performance}
	\begin{itemize}
	\item Sleep is essential for \textbf{memory consolidation, problem-solving, and emotional regulation}.
	\item Sleep deprivation leads to \textbf{cognitive decline, reduced neurogenesis, and poor decision-making}.
	\item \textbf{Solution:} Maintain \textbf{consistent sleep hygiene, exposure to natural light, and deep sleep optimization strategies}.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Mindfulness and Stress Resilience}
	\begin{itemize}
	\item Chronic stress impairs \textbf{cognition, immune function, and emotional well-being}.
	\item Mindfulness practices enhance \textbf{prefrontal cortex activity}, reducing stress and improving decision-making.
	\item \textbf{Solution:} Integrate \textbf{meditation, breathwork, and adaptive stress management techniques}.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Cognitive Load Management and Flow States}
	\begin{itemize}
	\item Multitasking and digital distractions increase \textbf{cognitive overload}, reducing productivity and creativity.
	\item Flow states enhance \textbf{focus, learning efficiency, and peak performance}.
	\item \textbf{Solution:} Use \textbf{deep work techniques, digital detox strategies, and structured routines} to achieve flow.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Biohacking for Mental and Physical Performance}
	\begin{itemize}
	\item Biohacking leverages \textbf{science-based interventions} to enhance cognitive and physical function.
	\item Techniques include \textbf{cold exposure, intermittent fasting, brain stimulation, and photobiomodulation}.
	\item \textbf{Solution:} Experiment with \textbf{safe and evidence-backed biohacking protocols} for optimization.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Behavioral Modification and Habit Formation}
	\begin{itemize}
	\item Long-term change requires \textbf{understanding behavioral psychology and habit formation principles}.
	\item Identity-based habits are more sustainable than outcome-based ones.
	\item \textbf{Solution:} Use \textbf{habit stacking, accountability systems, and environmental design} for effective change.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Daniel Schmachtenberger's findings from ChatGPT in general}

\end{center}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Emotional Regulation and Self-Mastery}
	\begin{itemize}
	\item Emotional intelligence is critical for \textbf{resilience, decision-making, and relationship management}.
	\item Suppressing emotions leads to \textbf{psychological stress and impaired cognitive performance}.
	\item \textbf{Solution:} Practice \textbf{emotional labeling, cognitive reframing, and somatic awareness} to regulate emotions effectively.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Memory Optimization and Learning Acceleration}
	\begin{itemize}
	\item Memory is enhanced by \textbf{association, visualization, and retrieval-based learning}.
	\item Passive learning is inefficient compared to \textbf{active recall and elaborative encoding}.
	\item \textbf{Solution:} Implement \textbf{memory palaces, chunking, and interleaved practice} for knowledge retention.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Gut-Brain Connection and Mental Performance}
	\begin{itemize}
	\item The gut microbiome influences \textbf{mood, cognition, and neuroinflammation}.
	\item Poor diet disrupts the \textbf{gut-brain axis}, leading to mental fog and fatigue.
	\item \textbf{Solution:} Support gut health through \textbf{probiotics, fiber-rich foods, and elimination of inflammatory substances}.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Harnessing Light and Circadian Rhythms}
	\begin{itemize}
	\item Circadian alignment optimizes \textbf{hormonal balance, energy levels, and cognitive function}.
	\item Artificial lighting disrupts \textbf{melatonin production}, leading to sleep and mood disorders.
	\item \textbf{Solution:} Align with natural light cycles, use \textbf{blue light blockers}, and optimize exposure to sunlight.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Psychotechnologies and Consciousness Expansion}
	\begin{itemize}
	\item Tools like \textbf{meditation, psychedelics, and neurofeedback} enhance self-awareness and perception.
	\item Altered states of consciousness can provide \textbf{deep insights and cognitive breakthroughs}.
	\item \textbf{Solution:} Use \textbf{safe, guided approaches} to explore altered states responsibly.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Resilience Through Anti-Fragility}
	\begin{itemize}
	\item True resilience isn’t about avoiding stress but \textbf{growing stronger through challenges}.
	\item Exposure to controlled stressors builds \textbf{mental toughness and adaptability}.
	\item \textbf{Solution:} Engage in \textbf{hormetic practices} like cold exposure, fasting, and cognitive stress training.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Digital Hygiene and Cognitive Clarity}
	\begin{itemize}
	\item Excessive screen time and notifications fragment \textbf{attention and cognitive bandwidth}.
	\item Information overload reduces \textbf{deep thinking and meaningful engagement}.
	\item \textbf{Solution:} Implement \textbf{screen time limits, notification control, and digital sabbaticals}.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Daniel Schmachtenberger's solutions}

\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Addressing Collective Blind Spots (Information Ecology)}
	\begin{itemize}
	\item Misinformation and cognitive biases degrade collective intelligence.
	\item Fragmented perspectives prevent accurate problem-solving.
	\item \textbf{Solution:} Develop \textbf{epistemic humility}, foster \textbf{sense-making communities}, and apply \textbf{cross-validation methods} to improve information quality.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Avoiding Perverse Incentives (Economic and Social Systems)}
	\begin{itemize}
	\item Many systemic issues arise from misaligned incentives that reward harmful behaviors.
	\item Short-term profit maximization leads to environmental and social degradation.
	\item \textbf{Solution:} Shift from \textbf{zero-sum competition} to \textbf{win-win collaboration} through regenerative economic models and aligned incentives.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Optimizing Health Through Multi-Scale Thinking}
	\begin{itemize}
	\item Treating symptoms rather than root causes leads to chronic health issues.
	\item Modern medicine often neglects systemic interactions between lifestyle, genetics, and environment.
	\item \textbf{Solution:} Use \textbf{networked health diagnostics}, personalized interventions, and \textbf{preventative strategies} to optimize well-being.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Enhancing Cognitive Sovereignty in a Digital Age}
	\begin{itemize}
	\item Social media and digital platforms fragment attention and manipulate perception.
	\item Algorithm-driven content shapes public opinion without transparency.
	\item \textbf{Solution:} Strengthen \textbf{cognitive sovereignty} through \textbf{attention discipline, deep work, and algorithmic literacy}.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Designing Resilient Societies (Meta-Crisis Solutions)}
	\begin{itemize}
	\item Civilization faces multiple existential risks, including climate collapse and AI misalignment.
	\item Current systems are fragile and prone to catastrophic failure.
	\item \textbf{Solution:} Implement \textbf{decentralized, adaptive governance} and \textbf{anti-fragile systems} that self-correct and promote long-term stability.
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large The Metacrisis: Making Sense in a Nonsensical World with Daniel Schmachtenberger \& Thomas Ermacora}

\end{center}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Introduction to the Meta-crisis}
	\begin{itemize}
	\item Describes the interconnected nature of the many crises facing society today
	\item Outlines the totality of risk that we face as a species and planet. 
	\item Climate change, Inequality, The rise of decentralized technology, and The fall of problem-solving
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{The Meta-crisis and Systemic Thinking}
	\begin{itemize}
	\item To solve elephants poaching, built bigger fences, the specific problem got solved.
	\item But did not address the core issue, ie poverty of the poachers.
	\item So, they went on poaching other animals.
	\item A holistic solution is needed, that's Systems Thinking
	\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Historical Lessons from Civilizational Collapse}
	\begin{itemize}
	\item Solving problems that are narrowly defined, cause wider implications outside.
	\item To solve problem of horse-shit, we invented cars, which then caused Climate change, global warming etc.
	\item Solving for village, country, planet? trade-offs at various level.
	\end{itemize}
\end{frame}


% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{frame}[fragile]\frametitle{Exponential Technology and Global Risks}
	% \begin{itemize}
	% \item 
	% \end{itemize}
% \end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{frame}[fragile]\frametitle{The Role of Financial and Material Systems in Crisis}
	% \begin{itemize}
	% \item 
	% \end{itemize}
% \end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{frame}[fragile]\frametitle{Environmental Boundaries and Human Impact}
	% \begin{itemize}
	% \item 
	% \end{itemize}
% \end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{frame}[fragile]\frametitle{The Third Attractor: A Framework for Solutions}
	% \begin{itemize}
	% \item 
	% \end{itemize}
% \end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{frame}[fragile]\frametitle{Exponential Growth and the Biosphere’s Limits}
	% \begin{itemize}
	% \item 
	% \end{itemize}
% \end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{frame}[fragile]\frametitle{The Collapse of Complex Societies}
	% \begin{itemize}
	% \item 
	% \end{itemize}
% \end{frame}


% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{frame}[fragile]\frametitle{Navigating the Metacrisis for Humanity’s Survival}
	% \begin{itemize}
	% \item 
	% \end{itemize}
% \end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Daniel Schmachtenberger | Reality, Meaning \& Self-Development | Modern Wisdom Podcast 179}

\end{center}
\end{frame}
