%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Jottings from Talks, Blogs}

{\small Ray Dalio}


\end{center}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Principles}

{\em “Principles are fundamental truths that serve as the foundations for behavior that gets you what you want out of life. They can be applied again and again in similar situations to help you achieve your goals.” }

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Build a machine (system)}

\begin{itemize}
\item Those who are most successful are capable of “higher level thinking” —i.e., they are able to step back and design a “machine” consisting of the right people doing the right things to get what they want. 
\item Visualize alternative machines and their outcomes, and then choose
\item Imagine how goals 1, 2, and 3 can be achieved. 
\item At the end of this process, your plan should look like a realistic movie script, which describes the parties and their interactions through time. 
\item Remember that everything takes longer and costs more than you plan for. 
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{5-step process to achieve goals}

\begin{itemize}
\item Setting goals
\item Perceiving problems
\item Diagnosis
\item Design
\item Doing the tasks
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Evaluate the believability of people}

\begin{itemize}
\item While it’s good to be open-minded and questioning, don’t treat all opinions as equally valuable. 
\item Almost everyone has an opinion, but many are worthless or harmful. 
\item The views of people without track records are not equal to the views of people with strong track records.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Realize that people's values and abilities are unlikely to change}

\begin{itemize}
\item Recognize that people are built very differently. 
\item Think about their very different values, abilities, and skills. 
\item In picking people for long-term relationships, values are most important, abilities come next, and skills are the least important.
\item Don’t believe it when someone caught being dishonest says they have seen the light and will never do that sort of thing again. Chances are they will. 
\item Know what makes your people tick, because people are your most important resource. 
\item If there are performance problems, it is either because of design problems (e.g., the person has too many responsibilities) or fit/abilities problems. Abilities can be improved by trainings.
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Trust yet control}

\begin{itemize}
\item Hold people accountable and appreciate them holding you accountable.
\item Constant examination of problems builds a sample size that helps point the way to a resolution and is a good way to detect problems early on before they become critical. 
\item Avoiding these daily conflicts produces huge costs in the end.
\item Even a tiny amount of cheating is intolerable, so your happiness and success will depend on your controls. 
\item Security controls should be viewed as a necessary tool of our profession, not as a personal affront to an individual’s integrity. 
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Seek Truth, as it will help you to identify problems and overcome them (This one is going to be LONG)}

\begin{itemize}
\item $Reality + Dreams + Determination = A Successful Life.$
\item Success is getting what you want
\item Those who react well to pain that stands in the way of getting to their goals, gain strength and satisfaction
\item Learning comes from making mistakes, reflecting on the causes of the mistakes, and learning what to do differently in the future
\item $Pain + Reflection = Progress$
\item Don’t tolerate badness.
\item Don’t use the anonymous “we” and “they,” because that masks personal responsibility—use specific names.
\end{itemize}

\end{frame}




