%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{1. Seek Wealth, Not Money or Status}
\begin{itemize}
\item Wealth is assets that earn while you sleep; e.g.
\begin{itemize}
\item Software earning commission per transaction, 
\item Mutual funds value growing up, 
\item House rent, etc.
\end{itemize}
\item Wealth buys your freedom.
\item Money is how we transfer wealth.
\item Money is not going to solve all of your problems; but it's going to solve all of your {\it money} problems.
\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{1. Seek Wealth, Not Money or Status}
\begin{itemize}
\item Status is your rank in the social hierarchy
\item Those who are not able to make money, play game of virtue, called {\it status}
\item Wealth is not a zero-sum game. 
\begin{itemize}
\item Everybody can have a house. 
\item My having house does not mean that you can not. 
\item But in stocks, if i earn someone else has lost it.
\end{itemize}
\item Status is a zero-sum game
\begin{itemize}
\item When someone is number one then the other has to be number two or lower. 
\item  To be the winner, there must be a loser. That's status.
\end{itemize}
\item People creating wealth will always be attacked by people playing status games
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{2. Make Abundance for the World}
\begin{itemize}
\item Wealth is not finite. Else, we all would be in caves, dividing fire wood.
\item Most wealth in civilization has been created.
\begin{itemize}
\item Got created from somewhere. 
\item Got created from people. 
\item Got created from technology. 
\item Got created from productivity. 
\item Got created from hard work.
\end{itemize}
\item Everyone can be rich
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{2. Make Abundance for the World}
\begin{itemize}
\item Wealth isn't about taking something from somebody else
\item Ethical wealth creation makes abundance for the world
\item Money historically treated as evil, 
\item Because you find people getting rich by taking work from poor. 
\item Exploitation: By a sword, or a gun, or taxes, or crony capitalism, or Communism. \item Like Parasites living off a tree.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{2. Make Abundance for the World}
\begin{itemize}
\item Now everyone is richer than anyone alive 200 years ago.
\item We all have vehicles, medicines, food, etc. They didn't.
\item ``Today, I would rather be a poor person in a First World country, than be a rich person in Louis the XIV's France''
\item In 20 years, most would be automated. 
\item Basics would be taken care. 
\item A Massive abundance.
\item We would do only creative pursuits.
\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{3. Free Markets Are Intrinsic to Humans}
\begin{itemize}
\item Capitalism [meaning: free markets] is intrinsic to the humans. 
\item We cooperate. 
\item Can keep track of debits and credits of work contributions and payments accordingly. 
\item That's ``Free Market Capitalism''.
\item We cant do all. 
\item So we cooperate and get what we don't make/do. 
\item We all have opportunity to produce/offer to others
\item If too many takers and not enough makers $\rightarrow$ ruin
\item Ideal society: free minds, and free markets. Small-scale exchange between humans that's voluntary,
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{4. Making Money Isn't About Luck}
\begin{itemize}
\item Luck should not be factor of your success.
\item Four types of Luck:
\begin{itemize}
\item Blind Luck: Like fortune, fate, comes without any control.
\item From Hustling (``fortune favors he brave''): Through persistence, hard work, hustle. Trying lots of things so that you get something.
\item From Preparation (``chance favors prepared mind''): Be very skilled in the field, you get better sense where fortune is.
\item From Unique Character: Because of unique/rare ability you go at such places where there is treasure, which no one can find.
\end{itemize}
\item Wealth stacks up one chip at a time, not all at once

\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{5. Make Luck Your Destiny}
\begin{itemize}
\item Build character where luck becomes deterministic, 
\item Opportunity finds you.
\item Build such a strong reputation/brand that everyone wants to work with you.
\item Dig deeper than other people do, 
\item Deeper than seems rational just because you're interested. 
\item ``Extreme people get extreme results.''
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{6. You Won't Get Rich Renting Out Your Time}
\begin{itemize}
\item Can't earn non-linearly while renting out time ie getting paid per hour.
\item There, when sleeping, you're not earning.
\item If your skills can be trained, then you are replaceable by another human or robot.
\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{7. Live Below Your Means for Freedom}
\begin{itemize}
\item People living below their means have freedom that those busy upgrading their lifestyle.
\item Live like before even after you make money. 
\item Only make it functionally comfortable.
\item Not for show-off of status. 
\item Status is zero sum game.
\item (If you are not richer than Bill Gates, you are poor. Then why go in that race which you are sure not to be even close.)
\item Typically money is made in discrete lumps, so that you don't upgrade your lifestyle overnight and erratically.
\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{8. Give Society What It Doesn't Know How to Get}
\begin{itemize}
\item Society will pay you for creating what it wants and delivering it at scale
\item Figure out what product you can provide and then figure out how to scale it
\item Steve Jobs figured out Smart Phone.
\item Solutions start with the rich, like chauffeur driven cars, then trickle to common man, with Uber platform, everyone has a chauffeur driven car. At scale.
\item ``Entrepreneurship is essentially an act of creating something new from scratch. Predicting that society will want it, and then figuring out how to scale it, and get it to everybody in a profitable way, in a self-sustaining way.''
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{9. The Internet Has Massively Broadened Career Possibilities}
\begin{itemize}
\item With Internet you can find audience for product/talent/skill no matter where you are.
\item Internet lets scaling of any niche obsession.
\item When you're competing with people it's because you're copying them. Don't.  
\item Just do your own thing.
\item No one can compete you, due to your original-ness
\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{10. Play Long-Term Games With Long-Term People}
\begin{itemize}
\item All returns in life come from compound interest in long-term games
\item Play long-term games with long-term people. Pick such industry
% \item Motivation has to come intrinsically
% \item Integrity is what someone does, despite what they say they do
\item Find people who seem irrationally ethical.
\item ``Self-esteem is the reputation that you have with yourself.'' You'll always know.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{12. Partner With Rational Optimists}
\begin{itemize}
\item Don't partner with cynics and pessimists.
\item We're genetically hardwired to be pessimists. 
\item But modern society is far, far safer. No tigers wandering around the street.
\item To create things, be a rational optimist. 
\item Rational to see the world for what it really is. 
\item Optimistic about your own capabilities to get things done.
\item``Either lead, follow, or get out of the way.'' 
\item Some people have 4th option: They tell that thing is not going to work.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{13. Arm Yourself With Specific Knowledge}
To make money \ldots
\begin{itemize}
\item You get rewarded by society for giving it what it wants and it doesn't know how to get elsewhere.
\item You need:
\begin{itemize}
\item Specific Knowledge: that only you know or only a small set of people know.
\item Accountability/Brand: you want to be known as the person who can deliver that.
\item Leverage/Amplification/Multiplier-effect: You need to have ways to scale your work without you and get paid passively.
\end{itemize}
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{Why: Specific Knowledge}
\begin{itemize}
\item Need to get paid at scale
\item Stand out of the crowd and get paid sustain-ably iff you have Specific Knowledge.
\item  Much easier to be top 5 percentile at three or four things than it is to be literally the number one at something
\item Specific knowledge comes on the job, not in a classroom.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{What: Specific Knowledge}
\begin{itemize}
\item Not trainable (else others can get it, so more supply, so reduced to margin play. Its no more ``mine' or ONLY I CAN DO)
\item Must Scale
\item Earns Passive income, while you are sleeping.
\item Has Leverage (ie amplification ie once created earns multiple times)
\item Low/Marginal cost of replication.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{How: Specific Knowledge}
\begin{itemize}
\item Genuine curiosity
\item Building judgment in a specific domain. 
\item Have intuition built. 
\item Been there done that type confidence.
\item Experiments in your field. 
\item Gain expertize by doing. 
\item The failures are learnings too.
\item Good, if, for that also, you can get paid.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{What: Leverage}
Types:
\begin{itemize}
\item Labor: someone else working for you and expanding your work. (Difficult)
\item Capital: Expand by putting more money, systems.
\item Products that have no marginal cost of replication: books, media, movies, and code.
\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{14. Specific Knowledge Is Highly Creative or Technical}
\begin{itemize}
\item Specific knowledge is on the bleeding edge of technology, art and communication
\item Specific knowledge can be taught only through apprenticeships, to an extent, on-job.
\item Specific knowledge is specific to the individual and situation
% \item You can't be too deliberate about assembling specific knowledge
\item Build specific knowledge where you are a natural.
\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{15. Learn to Sell, Learn to Build}
\begin{itemize}
\item Builders: CTOs, Engineers, workers
\item Sellers: Sales, Marketing, Advertising.
\item Steve Jobs and Steve Wozniak with Apple. CEO, CTO combo.
\item If you can do both, you will be unstoppable. Elon Musk.
\item ``I'd rather teach an engineer marketing than a marketer engineering'' - Bill Gates.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{16. Read What You Love Until You Love to Read}
\begin{itemize}
\item Have ability to pick up any book, read it and absorb it.
\item Avoid business magazines
\item Study microeconomics, game theory, psychology, persuasion, ethics, mathematics and computers.
\item ``Reading is faster than listening, doing is faster than watching.''
\item Read originals/classics eg Adam Smith's The Wealth of Nations, Darwin's Origin of the Species.
\item Don't fear any book. 
\item Retain good stuff and reject the bad.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{17. The Foundations Are Math and Logic}
\begin{itemize}
\item Mathematics and logic:  basis for understanding everything else
\item Foundational principles, (concepts, info arrangements) and algorithms.
\item Read a great book slowly than to skimming through hundreds quickly.
\item Understanding comes through repetition, usage,logic and foundations making you a smart thinker.
\item Learn persuasion and programming.
\item Need deep understanding of some complex topic.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{18. There's No Actual Skill Called `Business'}
\begin{itemize}
\item Avoid business schools and magazines
\item ``Case studies'' are just anecdotes, stories, other people's situations. 
\item Your stuff is different. Will understand only in real life.
\item Doing is faster than watching or listening. 
\item In videos/audios, can't change speed too much. You cannot go back. Hard to highlight, save to notebooks, etc.
\item The number of `doing' iterations drives the learning curve.
\item But not blind repetition of same things. 
\item Iterations are to be upgraded every time. (New weights after learning from back-propagation.)
\item Change approach every time.
\item If you're willing to bleed a little every day, you may win big later
\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{19. Embrace Accountability to Get Leverage}
\begin{itemize}
\item Take risks under your own name and society will reward you with leverage.
\item People who can fail in public have a lot of power.
\item Clear accountability is important. Without accountability, you don't have incentives, credibility.
\item A well-functioning team has clear accountability for each position.
\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{20. Take Accountability to Earn Equity}
\begin{itemize}
\item If you have high accountability, you're less replaceable
\item Accountability will get you equity.
\item The equity holders take on greater risk, but in exchange, they get nearly unlimited upside.
\item Accountability is reputation-al skin in the game
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{21. Labor and Capital Are Old Leverage}
\begin{itemize}
\item Everyone is fighting over labor and capital
\item Our brains aren't evolved to comprehend new forms of leverage
\item ``Fortunes require leverage. Business leverage comes from capital, people and products with no marginal costs of replication.''
\item Society over-values labor leverage. To get more done, employ more people.
\item Need actually less labor and more of other types of leverages to excel.
\item Managing people is hard. Avoid as much as possible.

\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{21. Labor and Capital Are Old Leverage}
\begin{itemize}
\item Capital, dominant leverage, of past.
\item To buy better technology (which is generally expensive).
\item To earn great amplification. With compounding effect.
\item Need specific knowledge and accountability to obtain capital
\item You get money from other based on your reputation.

\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{22. Product and Media Are New Leverage}
\begin{itemize}
\item Software and media can earn while you sleep
\item No permissions are needed use Code/media leverage.
\item Less/no marginal cost of replication.
% \item Meaning, you can multiply your efforts without having to involve other humans and without needing money from other humans.
\item All new fortunes can be made here.
\item Combining all three forms of leverage is a magic combination, a startup
\item Less but very smart engineers, VC capital for marketing/scaling and lots of code/media/content.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{23. Product Leverage is Egalitarian}
\begin{itemize}
\item Best products are for everyone (middle bell curve) and for middle class.
\item Product leverage is a positive-sum game (all gain)
\item (Worlds richest are using same Android OS as others. The Flat world!!)
\item Status goods are limited to a few people. But functionally need not be too great. Rolex watch still shows the same time. (But just a bit extra, or uncommon to fetch the premium).
% \item Creating wealth with product leads to more ethical wealth.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{24. Pick a Business Model with Leverage}
An ideal business model has:
\begin{itemize}
\item Network effects: value grows as the square of the customers, as each new user adds value to the existing users.
\item Zero marginal cost of reproduction: producing more is free
\item Scale economies: the more you produce, the cheaper it gets
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{25. Example: From Laborer to Entrepreneur}
Example: Housing Contractor
\begin{itemize}
\item Laborers get paid hourly and have low accountability
\item General contractors get equity, but they're also taking risk
\item Property developers pocket the profit by applying capital leverage
\item Architects, large developers and REITs are even higher in the stack
\item Real estate tech companies apply the maximum leverage.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{26. Judgment Is the Decisive Skill}
\begin{itemize}
\item ``If you're steering a big ship, if you're steering Google or Apple, and your judgment is 10 or 20 percent better than the next person's, society will literally pay you hundreds of millions of dollars more, because you're steering a \$100 billion ship.''
\item Judgment is knowing the long-term consequences of your actions
\item Without experience, judgment is often less than useless.
\item Folks with best judgment are least emotional
\item Emotions prevent you from seeing what's actually happening
\item Judgment: exercise of wisdom. 
% \item Wisdom comes from experience; and that experience can be accelerated through short iterations.
\item Top investors often sound like philosophers (wise, eovolved, `sorted')
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{27. Set an Aspirational Hourly Rate}
\begin{itemize}
\item Set and enforce an aspirational hourly rate.
\item Outsource tasks that cost less than your hourly rate.
\item ``My aspirational rate was \$5,000/hr'' - Naval (Btw, Naval, after extrapolation to year, which is multi million dollars, achieved it!!)
\item ``You should be working on your product and
getting product-market fit, and you should be exercising and eating healthy. That's about it. That's all you have time for while you're on this mission.''- Paul Graham
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{28. Work As Hard As You Can}
\begin{itemize}
\item If ``getting wealthy'' is your goal, you must work as hard 
\item But hard work is no substitute for who you work with and what you work on. Most important!!
\item  ``product-market-founder  fit'' : how well a founder is personally suited to the business.
\item No matter how high your bar is, raise it
\item Anything you have to do, get it done. Why wait? You're not getting any younger.
\item Impatience with actions, patience with results.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{29. Be Too Busy to ‘Do Coffee'}
\begin{itemize}
\item Ruthlessly decline meetings
\item Be too busy to `do coffee' while keeping an uncluttered calendar.
\item If someone wants a meeting, see if call is ok instead. 
\item If they want to call, see if email is ok instead.
\item If they want to email, see if sms is ok instead.
\item  Ignore most text messages—unless they're true emergencies.
\item Do walking meetings. Do standing meetings. Keep them short, actionable and small. 
\item Only meet if proof of work is ready, ie something working, not for ppt.
\item  Product progress is the entrepreneur's resume, unfake-able resume.
\item Avoid meetings to free your time and mind.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{30. Keep Redefining What You Do}
\begin{itemize}
\item Become the best in the world at what you do.
\item Keep redefining what you do until you're the best at what you do.
\item Keep changing approach until you're number one.
\item To be successful in life, get comfortable managing multi-variate problems
and multiple-objective functions at once. 
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{31. Escape Competition Through Authenticity}
\begin{itemize}
\item Nobody can compete with you on being you.
\item Competition will trap you in a lesser game
\item Get away from the specter of competition,its stressful and nerve-wracking but also will drive you to the wrong way.
\item If someone else starts firing rockets, Elon won't mind. He has his own mission. Mars. Whatever others may be doing, he is on it.
\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{32. Play Stupid Games, Win Stupid Prizes}
\begin{itemize}
\item Competition will blind you to greater games.
\item Those in direct competition, really aren't. Me too businesses. (Shallow margins. Volume - TCSs, Wipros, INfys or the world.)
\item They end up adjacent or slightly different. 
\item You're one step away from a completely different business.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{33. Eventually You Will Get What You Deserve}
\begin{itemize}
\item On a long enough timescale, you will get paid.
\item It takes time.
\item  Apply judgment, apply accountability, and apply the skill of reading.
\item What are you really good at, that the market values?
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{34. Reject Most Advice}
\begin{itemize}
\item Most advice is their winning lottery ticket numbers. 
\item It wont make you rich.
\item The best founders listen to everyone but make up their own mind.
\item Scott Adams - ``systems not goals''
\item Even these notes,  you should examine everything. If something doesn't feel true to you, put it down. Set it aside.
\item Advice offers anecdotes to recall later, when you get your own experience
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{35. A Calm Mind, a Fit Body, a House Full of Love}
\begin{itemize}
% \item When you're wealthy, you'll realize it wasn't what you were seeking.
\item Yes, money will solve all your money problems. But it doesn't get you everywhere. 
\item You're still the same person.  If
you're happy, you're happy. If you're unhappy, you're unhappy. If you're calm and fulfilled and peaceful,
you're still that same person.
\item A calm mind, a  fit body and a house full of love must be earned
\item A lot of divorces happen over money, a lot of battles happen over internal anger
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{36. There Are No Get Rich Quick Schemes}
\begin{itemize}
\item Get rich quick schemes are just someone else getting rich off  you.
\item We don't have ads because it would ruin our credibility. (Same for me on LinkedIn. I don't post someone else's job requirements. That smells foul money deal.)
\item . If I say, ''I know how to get rich, and I'm going to sell that to you,'' then it ruins it.
\item Anyone giving advice on how to get rich should have made their money elsewhere
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{37. Productize Yourself}
\begin{itemize}
\item Figure out what you're uniquely good at, and apply as much leverage as possible
\item Find hobbies that make you rich, fit and creative.
\item One that makes you money, one that makes you  fit, and one that
makes you smarter. 
\item (Say, Yoga can keep you fit throughout your life.)
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{38. Accountability Means Letting People Criticize You}
\begin{itemize}
\item You have to stick your neck out and be willing to fail publicly
\item Accountability means letting people criticize you.
\item Don't refuse to do things just because others can't do them
\item Realize your philanthropic vision by running a business.
\item Many non-profit efforts would be better off  as for-profit companies.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{39. We Should Eventually Be Working for Ourselves}
\begin{itemize}
\item Midlife can be the most fruitful time to apply this advice
\item But we will have to make sacrifices and take on more risk.
\item Look up the value chain to find leverage
\item You will do better in a small organization
\item The goal is that we are all working for ourselves
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{40. Being Ethical Is Long-Term Greedy}
\begin{itemize}
\item If you cut fair deals, you will get paid in the long run
\item Ethics isn't something you study; it's something you do
\item Trust leads to compounding relationships
\item Being ethical attracts other long-term players
\item Being ethical is long-term greedy
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{41. Envy Can Be Useful, or It Can Eat You Alive}
\begin{itemize}
\item Suffering through the wrong thing can motivate you to  find the right thing
\item But there are points in your life when it can be a powerful booster rocket.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{42. Principal-Agent Problem: Act Like an Owner}
\begin{itemize}
\item If you think and act like an owner, it's only a matter of time until you become an owner
\item A principal is an owner; an agent is an employee
\item A principal's incentives are different than an agent's incentives.
\item The principal/owner of the business wants what is best for the business and will make the most money. 
\item  The agent tries to please the principal or might make them personally the most money.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{42. Principal-Agent Problem: Act Like an Owner}
\begin{itemize}
\item Almost all human behavior can be explained by incentives.
\item When you do deals, it’s better to have the SAME (win-win) incentives.
\item Be generous with top lieutenants—in terms of ownership.
\item Over time you want them to be aligned with you.
\item If you’re an employee, think like a principal
\item In big firms, Principal and Agent are very separated. 
\item Deal with small firms to avoid the principal-agent problem
\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{43. Kelly Criterion: Avoid Ruin}
\begin{itemize}
\item Don’t bet everything on one big gamble. 
\item Be careful how much you bet each time, so you don’t lose the whole kitty.
\item Nassim Taleb: `` ergodicity'': What is true for 100 people on average isn’t the same as one person averaging that same thing 100 times. (one go vs 100 in sequence)
% \item So risk-taking—especially when the averages that are
% calculated across large populations—is not always rational. 
\item If chances of winning are 50\% over population, then on a day, you may just lose, fully, thats it. Cant play anymore.
\item Don't cut corners and doing unethical or downright illegal things. You will be in jail for a small risk/gain. Game over.
\item Ruining your reputation is the same as getting wiped to zero.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{44. Schelling Point: Cooperating Without Communicating}
\begin{itemize}
\item In a multiplayer game, people respond based on what they think the other person’s response will be.
\item Shelling formulation:  How do you get people who cannot communicate with each other to coordinate?
\item Competing companies can settle at common price without communication, assuming both are rational. (Nash Equilibrium)
\item Use social norms to cooperate when you can’t communicate
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{45. Turn Short-Term Games Into Long-Term Games}
\begin{itemize}
\item Improve your leverage by turning short-term relationships into long-term ones
\item Pareto superior means something is better in some ways while being equal or better in other ways. It’s
not worse in any way. Useful in negotiations.
\item Pareto optimal is when the solution is the best it can possibly be and you can’t change it without making
it worse in at least one dimension. There is a hard trade-o  from this point forward.
\item . If you want something too badly, the other person can extract more value from you.
\item if someone is taking advantage, make short-term to long term. Make it repeat game. (??)
\item  Try to bring reputation into the negotiation.
Try to include other people who may want to play games with this person in the future.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{45. Turn Short-Term Games Into Long-Term Games}
\begin{itemize}
\item Convert single-move games to multi-move games
\item  “Actually, I need two different projects done. The  first project we’ll do
together, and based on that I’ll decide if we do the second project.”
\item  “I’m going to do this project with you, and I have three friends who want projects
done who are waiting to see the outcome of this project.”
\item Another way to address, you being taken advantage of, is to write public review.
\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{46. Compounding Relationships Make Life Easier}
\begin{itemize}
\item Life gets a lot easier when you know someone’s got your back
\item Mutual trust makes it easy to do business
\item If you are dealing with someone of 20 years of trust, you don't read contracts.
\item The most under-recognized reason startups fail is because the founders fall apart.
\item It’s better to have a few compounding relationships than many shallow ones
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{47. Price Discrimination: Charge Some People More}
\begin{itemize}
\item You can charge people for extras based on their propensity/ability to pay
\item Price discrimination is a technique for charging certain people more, with something extra.
\item Business-class seats routinely cost  ve or 10 times more than economy seats. But it costs the airline
much less—maybe two or three times more than a standard seat—to provide perks like wider seats, more
legroom and free drinks.
\item Rich people and large enterprises are willing to pay more, so price discrimination works. They need a bit extra facility and status signal.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{48. Consumer Surplus: Getting More Than You Paid For}
\begin{itemize}
\item People are willing to pay more than what companies charge
\item Consumer surplus is the excess
value you get from something when you pay less than you were willing to pay.
\item Although well-to-do people can pay \$20 for Starbucks coffee, it is still kept at \$5 for general consumers. So rich are  getting a lot of consumer surplus out of the coffee.  
\item A lot of
people are willing to pay more than what Amazon charges.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{49. Net Present Value: What Future Income Is Worth Today}
\begin{itemize}
\item See what future income is worth today by applying a discount to its future value
\item NPV: That stream of payments I’m going to get in the future—
what’s it worth today?
\item Apply this for any future payments, valuations, corpus needed to survive, etc.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{50. Externalities: Calculating the Hidden Costs of Products}
\begin{itemize}
\item Externalities let you account for the true cost of products by including hidden costs
\item  An externality is where there’s an additional cost imposed by whatever product is being produced
or consumed, that’s not accounted for in the price of the product. Say, destroying environment.
\item Pricing externalities is more effective than feel-good measures. 
\item Because the environment is  finite and precious, price it properly and include into the
cost of products and services.
\end{itemize}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{Bonus: Finding Time to Invest in Yourself}
\begin{itemize}
\item If you have to work a “normal job,” take on accountability to build your specific knowledge
\item You will need to rent your time to get started.
This is only acceptable when you are learning and saving.
\item Chief of staff  for a founder is one of the most coveted jobs for young people starting out in Silicon Valley.
\item Find the part of the job with the steepest learning curve
\item Develop a founder mentality
\item Accountability is something you can take on immediately
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{Bonus: Finding Time to Invest in Yourself}
\begin{itemize}
\item Specific knowledge can be timely or timeless
\item Machine learning is currently on top of the hype cycle. 
\item Later it may be very common; the world may have moved on to something else. That’s timely knowledge.
\item If you’re good at persuading people (or simplifying things for others, teaching), It’s always going to apply. That’s timeless knowledge.
\item You need combo. Scott Adams - ``You might combine persuasion with accounting and an
understanding of semiconductor production lines. Now you can become the best semiconductor salesperson and, later on, the best semiconductor company CEO.''
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{Bonus: Finding Time to Invest in Yourself}
\begin{itemize}
\item Danny Hillis - ``Technology is everything that doesn’t work yet.''
\item Technology is: how to mass produce or create efficiently and commercially for everybody.
\item Technology, a great field where you can pick up specific knowledge that is valuable to society.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{Bonus: Finding Time to Invest in Yourself}
\begin{itemize}
\item If you don’t have accountability, do something different
% \item Companies don’t know
% how to measure outputs, so they measure inputs instead.
\item Work in a way that your outputs are visible and
measurable. 
\item   From the agricultural and industrial ages: input hours were proxy for what kind of output you’d get.  its linear.
\item Today, it’s extremely nonlinear. One good investment decision can make a company $10 million or $100
million. 
\item One good product feature can be the difference between product-market fit and complete failure
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{Bonus: Finding Time to Invest in Yourself}
\begin{itemize}
\item As a result, judgment and accountability matter much more. 
\item Often the best engineers aren’t the hardest
workers. Sometimes they don’t work very hard at all, but they dependably ship that one critical product at just the right time
\item People need to be able to tell what role you had in the company’s success. 
\item You’ll develop thick-skin if you take on accountability, as both good and bad things come your way.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{References}
\begin{itemize}
\item Blog https://nav.al/rich
\item Youtube Channel ``Naval'', Playlist ``How to get rich''
\end{itemize}
\end{frame}